This code is for use in R to provide the analysis that contributed to the manuscript "Using the National Neonatal Audit Programme (NNAP) to assess the relationship between quality of antenatal and neonatal care with neonatal mortality"

MBRRACE data is downloaded from csv through the online data viewer tool:
https://timms.le.ac.uk/mbrrace-uk-perinatal-mortality/data-viewer/

Download the csv files for total mortality and place them in a folder named "MBRRACE_raw_data/total_mortality" in your working directory

NNAP data is downloaded 
https://www.rcpch.ac.uk/work-we-do/clinical-audits/nnap/data-access

Place NNAP csv files in a folder named "NNAP_raw_data" in your working directory

Ensure the following files are downloaded from the main github page and placed into the correct directory within your working directory:
"manual_unit_level_definition/NNAP_manual_unit_levels_to_add.csv"
"Linking_hospitals_to/hospital_trust_manual_linkage_sheet_master.csv"

```{r, load all the NNAP data frames}
library(readxl)
library(stringr) # For easy string manipulation (cleaning file names)
library(dplyr)
# ----------------------------------------------------------------------
# 1. Configuration
# ----------------------------------------------------------------------

# Define the folder containing the Excel files
# IMPORTANT: Replace "path/to/your/NNAP_raw_data" with the actual path
folder_path <- "NNAP_raw_data"

# Check if the folder exists before proceeding
if (!dir.exists(folder_path)) {
  stop(paste("Error: The folder '", folder_path, "' does not exist. Please check the path."))
}

# ----------------------------------------------------------------------
# 2. Find all Excel files
# ----------------------------------------------------------------------

# List all files ending with .xlsx or .xls (case-insensitive)
excel_files <- list.files(
  path = folder_path,
  pattern = "\\.(xlsx|xls)$",
  full.names = TRUE,
  ignore.case = TRUE
)

# Check if any files were found
if (length(excel_files) == 0) {
  message(paste("No Excel files found in:", folder_path))
} else {
  message(paste(length(excel_files), "Excel files found. Starting conversion..."))
}

# ----------------------------------------------------------------------
# 3. Loop through files and sheets
# ----------------------------------------------------------------------

# Iterate over each Excel file path
for (file_path in excel_files) {

  # Extract the base filename (e.g., "my_data_file.xlsx")
  file_name_full <- basename(file_path)

  # Remove the extension to get the base name (e.g., "my_data_file")
  file_name_base <- sub("\\.(xlsx|xls)$", "", file_name_full, ignore.case = TRUE)

  # Clean the base name for R variable use:
  # 1. Replace any non-alphanumeric characters (including spaces, hyphens) with underscores.
  clean_file_name <- str_replace_all(file_name_base, "[^[:alnum:]_]", "_")
  # 2. Replace multiple underscores with a single underscore.
  clean_file_name <- str_replace_all(clean_file_name, "_+", "_")
  # 3. Remove leading and trailing underscores using regex replacement.
  clean_file_name <- str_replace_all(clean_file_name, "^_+|_+$", "")

  # Extract the year (four digits) from the clean file name
  # Using str_extract to get a single string result for the year
  year_match <- str_extract(clean_file_name, "\\d{4}")
  
  # Set the year value, defaulting to 'Unknown' if no four-digit pattern is found
  year_to_add <- ifelse(is.na(year_match), "UnknownYear", year_match)

  # Get the names of all sheets in the current file
  sheets <- excel_sheets(file_path)

  message(paste("Processing file:", file_name_full, "with", length(sheets), "sheets."))

  # Iterate over each sheet name
  for (sheet_name in sheets) {

    # Clean the sheet name for R variable use (similar logic as filename)
    clean_sheet_name <- str_replace_all(sheet_name, "[^[:alnum:]_]", "_")
    clean_sheet_name <- str_replace_all(clean_sheet_name, "_+", "_")
    # Remove leading and trailing underscores using regex replacement.
    clean_sheet_name <- str_replace_all(clean_sheet_name, "^_+|_+$", "")

    # Construct the final dataframe name: filename_tabname
    df_name <- paste0(clean_file_name, "_", clean_sheet_name)

    # Read the sheet data into a temporary dataframe
    # The 'col_names = TRUE' assumes the first row is the header
    tryCatch({
      data_frame <- read_excel(
        path = file_path,
        sheet = sheet_name,
        col_names = TRUE
      )
      
      # Add the extracted year as a new column for record-keeping
      data_frame$Year <- year_to_add
      
      # --- Start Column Renaming Logic ---
      # need to list here all names of columns that need to be converted to UnitName
      columns_to_rename_to_Unit_name <- 
        c(
          "Place of birth name",
          "Placeofbirthname",
          "Provider Name",
          "Provider name",
          "ProviderName",
          "Providername",
          "Provider at 48 hours",
          "Providerat48hours",
          "Hospital of final discharge",
          "Hospitaloffinaldischarge",
          "Unit name",
          "Unitname",
          "UnitName",
          " UnitName",
          ".UnitName",
          "Name"
        )
      
      data_frame <- data_frame %>%
        rename(Unit_name = any_of(columns_to_rename_to_Unit_name))
      
      if ("Unit_name" %in% names(data_frame)) {
        
        # Trim leading/trailing spaces
        data_frame$Unit_name <- trimws(data_frame$Unit_name) # that doesn't seem to work
        #remove all spaces
        data_frame$Unit_name <- gsub(" ", "", data_frame$Unit_name) #this still doesn't quite work when there is a trailling space in a column name, so in the code below I have sometimes had to tweak the unit_name column when copying it across to simpler sheets
        data_frame$` UnitName` <- data_frame$Unit_name #therefore we just manually tweak the name of the column here
        
        # Replace & with AND
        data_frame$Unit_name <- gsub("&", "AND", data_frame$Unit_name)
        data_frame$Unit_name <- gsub("[()]", "", data_frame$Unit_name)
        
        #irritatingly, we need another clause in here that sorts out a unique problem in 2017 when GLAN CLWYD HOSPITAL and QUEEN'S HOSPITAL, BURTON ON TRENT and WREXHAM MAELOR HOSPITAL all need concatenating to the column "Place of birth level" or "Provider level" if it exists. We then DO NOT want to remove NICU LNU or SCBU from the name YET like I did in previous iterations because these names are important - some hospitals might have two entries in NNAP depending upon their level. It just means the linkage spreadsheet later on needs to reflect level as well as hospital
        if ("Place of birth level" %in% names(data_frame)) {
          data_frame$Unit_name <-
            paste0(data_frame$Unit_name, "_", data_frame$`Place of birth level`)
        }
        if ("Provider level" %in% names(data_frame)) {
          data_frame$Unit_name <-
            paste0(data_frame$Unit_name, "_", data_frame$`Provider level`)
        }
        

      }

      
      #get rid of any spaces and insert an underscore
      names(data_frame) <- gsub(" ", "_", names(data_frame))
      
      
      # 1. Define columns to keep unchanged (key identifiers and the new 'Year' column)
      # Ensure "Unit_name" and "Year" are always in the exclusion list as requested
      columns_to_exclude <- 
        c(
          "Unit_name",  
          "Year")
      
      # 2. Get all current column names
      current_cols <- names(data_frame)
      
      # 3. Identify the columns that *should* be renamed (those NOT in the exclusion list)
      cols_to_rename <- current_cols[!(current_cols %in% columns_to_exclude)]
      
      # 4. Define the suffix (using the clean sheet name, preceded by an underscore)
      sheet_suffix <- paste0("_", clean_sheet_name)
      
      # 5. Create the new names for the columns that should be renamed
      # New name = original column name + sheet_suffix (e.g., Value_Sales_Data)
      new_names <- paste0(cols_to_rename, sheet_suffix)
      
      # 6. Apply the new names to the dataframe's column list
      # The 'match' function is used to find the positions of the columns being renamed.
      names(data_frame)[match(cols_to_rename, current_cols)] <- new_names
      
      if ("Unit_name" %in% names(data_frame)) { #only do the following if the Unit_name column exists
      #manually adjust the Unit_name column to get rid of all of the spaces, punctuation and make it capital letters
      data_frame$Unit_name <- 
        toupper(
          gsub("[[:space:][:punct:]]", "", data_frame$Unit_name))
      }
      
      # --- End Column Renaming Logic ---

      # Assign the temporary dataframe to the dynamically generated name in the global environment
      assign(df_name, data_frame, envir = .GlobalEnv)

      message(paste("  -> Successfully created dataframe:", df_name))

    }, error = function(e) {
      warning(paste("  -> Skipping sheet '", sheet_name, "' due to error:", e$message))
    })
  }
}

# ----------------------------------------------------------------------
# 4. Final Verification (Optional)
# ----------------------------------------------------------------------

message("\nConversion complete.")
# To check all new dataframes created, you can use:
# new_dfs <- ls(pattern = "^NNAP_.*")
# print(new_dfs)

# Example: If you had a file called 'Report Q3.xlsx' with a sheet 'Sales Data',
# the resulting dataframe would be named 'Report_Q3_Sales_Data'.
# If that sheet had a column 'Value', it is now named 'Value_Sales_Data'.


```


Extract the level of the unit


```{r, 2017 unit level}
nnap_2017_unit_level <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Bronchopulmonary_dysplasia$Unit_name,
    Unit_level=
      as.character(nnap_2017_data_0_Bronchopulmonary_dysplasia$Place_of_birth_level_Bronchopulmonary_dysplasia)
  )

nnap_2017_unit_level$Unit_level <-
  ifelse(nnap_2017_unit_level$Unit_level=="SCU", 1, nnap_2017_unit_level$Unit_level)
nnap_2017_unit_level$Unit_level <-
  ifelse(nnap_2017_unit_level$Unit_level=="LNU", 2, nnap_2017_unit_level$Unit_level)
nnap_2017_unit_level$Unit_level <-
  ifelse(nnap_2017_unit_level$Unit_level=="NICU", 3, nnap_2017_unit_level$Unit_level)

#correct crosshouse in Ayrshire to a level 2 unit as it hasnt ever provided true level 3 care (This is within NHS Ayrshire and Arran)
nnap_2017_unit_level$Unit_level <- 
  ifelse(nnap_2017_unit_level$Unit_name=="AYRSHIREMATERNITYUNITCROSSHOUSENICU", 2, nnap_2017_unit_level$Unit_level)

#correct victoria hospital fife to a level 2 unit as it hasnt ever provided true level 3 care (This is within NHS fife)
nnap_2017_unit_level$Unit_level <- 
  ifelse(nnap_2017_unit_level$Unit_name=="VICTORIAHOSPITALFIFENICU", 2, nnap_2017_unit_level$Unit_level)

#wrexham hospital has never been a level 3 neonatal unit 
nnap_2017_unit_level$Unit_level <- 
  ifelse(nnap_2017_unit_level$Unit_name=="WREXHAMMAELORHOSPITALNICU", 2, nnap_2017_unit_level$Unit_level)

#Raigmore hospital in inverness has never been a level 3 neonatal unit, this is in Inverness part of NHS Highlands
nnap_2017_unit_level$Unit_level <- 
  ifelse(nnap_2017_unit_level$Unit_name=="RAIGMOREHOSPITALINVERNESSNICU", 2, nnap_2017_unit_level$Unit_level)

#Glanclwyd hospital in inverness has never been a level 3 neonatal unit, this is in Inverness part of NHS Highlands
nnap_2017_unit_level$Unit_level <- 
  ifelse(nnap_2017_unit_level$Unit_name=="GLANCLWYDHOSPITALNICU", 2, nnap_2017_unit_level$Unit_level)

#university hospital north tees has never been a level 3 NICU UNIVERSITYHOSPITALOFNORTHTEESNICU
nnap_2017_unit_level$Unit_level <- 
  ifelse(nnap_2017_unit_level$Unit_name=="UNIVERSITYHOSPITALOFNORTHTEESNICU", 2, nnap_2017_unit_level$Unit_level)

```

```{r, 2018 unit level}
nnap_2018_unit_level <-
  data.frame(
    
    Unit_name=
      gsub("\\d", "", x=nnap_2018_data_Bronchopulmonary_dysplasia$Unit_name),
    Unit_level=
      as.character(nnap_2018_data_Bronchopulmonary_dysplasia$Provider_level_Bronchopulmonary_dysplasia)
  )

#correct crosshouse in Ayrshire to a level 2 unit as it hasnt ever provided true level 3 care (This is within NHS Ayrshire and Arran)
nnap_2018_unit_level$Unit_level <- 
  ifelse(nnap_2018_unit_level$Unit_name=="AYRSHIREMATERNITYUNITCROSSHOUSE", 2, nnap_2018_unit_level$Unit_level)
#correct victoria hospital fife to a level 2 unit as it hasnt ever provided true level 3 care (This is within NHS fife)
nnap_2018_unit_level$Unit_level <- 
  ifelse(nnap_2018_unit_level$Unit_name=="VICTORIAHOSPITALFIFE", 2, nnap_2018_unit_level$Unit_level)

#university hospital north tees has never been a level 3 NICU UNIVERSITYHOSPITALOFNORTHTEESNICU
nnap_2018_unit_level$Unit_level <- 
  ifelse(nnap_2018_unit_level$Unit_name=="UNIVERSITYHOSPITALOFNORTHTEES", 2, nnap_2018_unit_level$Unit_level)
```

```{r, 2022 unit level}
nnap_2022_unit_level <- data.frame(
  Unit_name = nnap_2022_data_0_BPD$Unit_name,
  
  Unit_level = NA,
  row.names = NULL
)



nnap_2022_unit_level <- nnap_2022_unit_level %>%
  mutate(
    Unit_level = case_when(
      grepl("SCBU", Unit_name) ~ "1",
      grepl("LNU",  Unit_name) ~ "2",
      grepl("NICU", Unit_name) ~ "3",
      TRUE ~ NA_character_
    )
  )

#nnap_2022_unit_level$Unit_level_check_NICU <- 
#  grepl(x=nnap_2022_unit_level$Unit_name, pattern="NICU")

table(nnap_2022_unit_level$Unit_level)
```

```{r, 2023 unit level}
nnap_2023_unit_level <-
  data.frame(
    
    Unit_name=
      nnap_2023_data_masked_BPD$Unit_name,
    Unit_level=
      as.character(nnap_2023_data_masked_BPD$Unit_level_BPD)
  )


#correct victoria hospital fife to a level 2 unit as it hasnt ever provided true level 3 care (This is within NHS fife)
nnap_2023_unit_level$Unit_level <- 
  ifelse(nnap_2023_unit_level$Unit_name=="VICTORIAHOSPITALKIRKCALDY", 2, nnap_2023_unit_level$Unit_level)
```

```{r, 2019 unit level}
nnap_2019_unit_level <- nnap_2023_unit_level
```

```{r, 2020 unit level}
nnap_2020_unit_level <- nnap_2023_unit_level
```

```{r, 2021 unit level}
nnap_2021_unit_level <- nnap_2023_unit_level
```

Extract the BPD data for each year first

```{r, 2017 bpd}
nnap_2017_bpd_workings <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Bronchopulmonary_dysplasia$Unit_name,
    bpd_n_eligible=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`Number_of_eligible_babies_Bronchopulmonary_dysplasia`),

    bpd_n_with_bpd_data_and_alive=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`With_outcome_Bronchopulmonary_dysplasia`),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`Missing_number_Bronchopulmonary_dysplasia`),
    bpd_n_with_bpd_data_and_died=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`Died_number_Bronchopulmonary_dysplasia`),

    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`No_BPD_Bronchopulmonary_dysplasia`),
    bpd_n_mild_bpd=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`Mild_BPD_Bronchopulmonary_dysplasia`),
    bpd_n_significant_bpd=
      as.numeric(nnap_2017_data_0_Bronchopulmonary_dysplasia$`Significant_BPD_number_Bronchopulmonary_dysplasia`)
)

nnap_2017_bpd_workings$check_missing <- 
  as.numeric(nnap_2017_bpd_workings$bpd_n_eligible) - 
  as.numeric(nnap_2017_bpd_workings$bpd_n_with_bpd_data_and_alive) - 
  as.numeric(nnap_2017_bpd_workings$bpd_n_alive_and_missing_bpd_data) -
  as.numeric(nnap_2017_bpd_workings$bpd_n_with_bpd_data_and_died) 


nnap_2017_bpd_workings$check_bpd_severity <- 
  as.numeric(nnap_2017_bpd_workings$bpd_n_with_bpd_data_and_alive) - 
  as.numeric(nnap_2017_bpd_workings$bpd_n_alive_and_no_bpd) - 
  as.numeric(nnap_2017_bpd_workings$bpd_n_mild_bpd) - 
  as.numeric(nnap_2017_bpd_workings$bpd_n_significant_bpd) 

nnap_2017_bpd_workings$bpd_n_alive_and_yes_bpd <-
  as.numeric(nnap_2017_bpd_workings$bpd_n_mild_bpd) +
  as.numeric(nnap_2017_bpd_workings$bpd_n_significant_bpd) 

nnap_2017_bpd <-
  data.frame(
    Unit_name=
      nnap_2017_bpd_workings$Unit_name,
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2017_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2017_bpd_workings$bpd_n_alive_and_yes_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2017_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2017_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )
```

```{r, 2018 bpd}
nnap_2018_bpd_workings <-
  data.frame(
    Unit_name=
      nnap_2018_data_Bronchopulmonary_dysplasia$Unit_name,
    bpd_n_eligible=
      as.numeric(nnap_2018_data_Bronchopulmonary_dysplasia$`Number_eligible_babies_Bronchopulmonary_dysplasia`),

    bpd_n_with_bpd_data_and_alive=
      as.numeric(nnap_2018_data_Bronchopulmonary_dysplasia$NonMissing_Bronchopulmonary_dysplasia),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2018_data_Bronchopulmonary_dysplasia$Missing_Bronchopulmonary_dysplasia),
    bpd_n_with_bpd_data_and_died=
      as.numeric(nnap_2018_data_Bronchopulmonary_dysplasia$Death_brf_36_Bronchopulmonary_dysplasia),

    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2018_data_Bronchopulmonary_dysplasia$No_BPD_Bronchopulmonary_dysplasia),
    bpd_n_any_bpd=
      as.numeric(nnap_2018_data_Bronchopulmonary_dysplasia$BPD_Bronchopulmonary_dysplasia)
)

nnap_2018_bpd <-
  data.frame(
    Unit_name=
      gsub("\\d", "", x=nnap_2018_bpd_workings$Unit_name),
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2018_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2018_bpd_workings$bpd_n_any_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2018_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2018_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )
```

```{r, 2019 bpd}
nnap_2019_bpd_workings <-
  data.frame(
    Unit_name=
      nnap_2019_data_BPD$Unit_name,
    
    bpd_n_eligible=
      as.numeric(nnap_2019_data_BPD$Number_of_eligible_babies_BPD),
    
    bpd_n_alive_and_missing_bpd_data=
        as.numeric(
          sub(" .*", "", nnap_2019_data_BPD$`Missing_Data_(%)_BPD`)
        ),
    
    bpd_n_with_bpd_data_and_died=
        as.numeric(
          sub(" .*", "", nnap_2019_data_BPD$`Number_of_deaths_before_36_weeks_cga_(%)_BPD`)
        ),

    bpd_n_alive_and_no_bpd=
        as.numeric(
          sub(" .*", "", nnap_2019_data_BPD$`No_BPD_(%)_BPD`)
        ),

    bpd_n_any_bpd=
        as.numeric(
          sub(" .*", "", nnap_2019_data_BPD$`BPD_(%)_BPD`)
        )
)

nnap_2019_bpd <-
  data.frame(
    Unit_name=
      nnap_2019_bpd_workings$Unit_name,
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2019_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2019_bpd_workings$bpd_n_any_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2019_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2019_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )
```

```{r, 2020 bpd}
nnap_2020_bpd_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_BPD$Unit_name,
    
    bpd_n_eligible=
      as.numeric(nnap_2020_data_BPD$Number_of_eligible_babies_BPD),
    
    bpd_n_alive_and_missing_bpd_data=
        as.numeric(
          sub(" .*", "", nnap_2020_data_BPD$`Missing_Data_(%)_BPD`)
        ),
    
    bpd_n_with_bpd_data_and_died=
        as.numeric(
          sub(" .*", "", nnap_2020_data_BPD$`Number_of_deaths_before_36_weeks_cga_(%)_BPD`)
        ),

    bpd_n_alive_and_no_bpd=
        as.numeric(
          sub(" .*", "", nnap_2020_data_BPD$`No_BPD_(%)_BPD`)
        ),

    bpd_n_any_bpd=
        as.numeric(
          sub(" .*", "", nnap_2020_data_BPD$`BPD_(%)_BPD`)
        )
)

nnap_2020_bpd <-
  data.frame(
    Unit_name=
      nnap_2020_bpd_workings$Unit_name,
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2020_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2020_bpd_workings$bpd_n_any_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2020_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2020_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )
```

```{r, 2021 bpd}
nnap_2021_bpd_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_BPD$Unit_name,
    
    bpd_n_eligible=
      as.numeric(nnap_2021_data_BPD$Number_of_eligible_babies_BPD),
    
    bpd_n_alive_and_missing_bpd_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_BPD$`Missing_Data_(%)_BPD`)
        ),
    
    bpd_n_with_bpd_data_and_died=
        as.numeric(
          sub(" .*", "", nnap_2021_data_BPD$`Number_of_deaths_before_36_weeks_cga_(%)_BPD`)
        ),

    bpd_n_alive_and_no_bpd=
        as.numeric(
          sub(" .*", "", nnap_2021_data_BPD$`No_BPD_(%)_BPD`)
        ),

    bpd_n_any_bpd=
        as.numeric(
          sub(" .*", "", nnap_2021_data_BPD$`BPD_(%)_BPD`)
        )
)

nnap_2021_bpd <-
  data.frame(
    Unit_name=
      nnap_2021_bpd_workings$Unit_name,
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2021_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2021_bpd_workings$bpd_n_any_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2021_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2021_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )
```

```{r, 2022 bpd}
nnap_2022_bpd_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_BPD$Unit_name,
    
    bpd_n_alive_and_dead_with_bpd_data=
      as.numeric(nnap_2022_data_0_BPD$NumberOfEligibleBabies_BPD),
    
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2022_data_0_BPD$NotDeterminable_BPD),
    
    bpd_n_with_bpd_data_and_died=
      as.numeric(nnap_2022_data_0_BPD$DeadBefore36_BPD),

    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2022_data_0_BPD$None_BPD),

    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2022_data_0_BPD$BPD_BPD)
)

nnap_2022_bpd <-
  data.frame(
    Unit_name=
      nnap_2022_bpd_workings$Unit_name,
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2022_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2022_bpd_workings$bpd_n_alive_and_yes_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2022_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2022_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )
```

```{r, 2023 bpd}
nnap_2023_bpd_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_BPD$Unit_name,
    
    bpd_n_alive_and_dead_eligible_for_bpd_data=
      as.numeric(nnap_2023_data_masked_BPD$Eligible_BPD),
    
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2023_data_masked_BPD$Indeterminable_BPD),
    
    bpd_n_with_bpd_data_and_died=
      as.numeric(nnap_2023_data_masked_BPD$Early_death_BPD),

    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2023_data_masked_BPD$No_BPD_BPD),

    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2023_data_masked_BPD$BPD_BPD)
)

nnap_2023_bpd_workings$bpn_n_alive_and_eligible <-
  nnap_2023_bpd_workings$bpd_n_alive_and_dead_eligible_for_bpd_data - nnap_2023_bpd_workings$bpd_n_with_bpd_data_and_died

nnap_2023_bpd <-
  data.frame(
    Unit_name=
      nnap_2023_bpd_workings$Unit_name,
    bpn_n_alive_and_eligible=
      as.numeric(nnap_2023_bpd_workings$bpn_n_alive_and_eligible),
    bpd_n_alive_and_yes_bpd=
      as.numeric(nnap_2023_bpd_workings$bpd_n_alive_and_yes_bpd),
    bpd_n_alive_and_no_bpd=
      as.numeric(nnap_2023_bpd_workings$bpd_n_alive_and_no_bpd),
    bpd_n_alive_and_missing_bpd_data=
      as.numeric(nnap_2023_bpd_workings$bpd_n_alive_and_missing_bpd_data)
  )

```

**************************
Extract the NEC data for each year
**************************

```{r, 2017 NEC}
nnap_2017_NEC_workings <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Necrotising_enterocolitis$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$Number_of_eligible_babies_Necrotising_enterocolitis),
    NEC_n_with_NEC_data=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$With_outcome_Necrotising_enterocolitis),
    NEC_n_alive_and_missing_NEC_data=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$Missing_alive_number_Necrotising_enterocolitis),
    NEC_n_dead_and_missing_NEC_data=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$Missing_died_number_Necrotising_enterocolitis),
    NEC_n_with_NEC_data_no_and_died_of_something_else=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$Died_prior_to_discharge_home_but_had_no_NEC_Necrotising_enterocolitis),
    
    NEC_n_NEC_yes=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$NEC_number_Necrotising_enterocolitis),
    NEC_n_alive_and_NEC_no=
      as.numeric(nnap_2017_data_0_Necrotising_enterocolitis$No_NEC_Necrotising_enterocolitis)
)

nnap_2017_NEC_workings$NEC_n_NEC_no <-
  nnap_2017_NEC_workings$NEC_n_with_NEC_data_no_and_died_of_something_else +
  nnap_2017_NEC_workings$NEC_n_alive_and_NEC_no

nnap_2017_NEC_workings$missing_NEC_data <-
  nnap_2017_NEC_workings$NEC_n_alive_and_missing_NEC_data + nnap_2017_NEC_workings$NEC_n_dead_and_missing_NEC_data

nnap_2017_NEC <-
  data.frame(
    Unit_name=
      nnap_2017_NEC_workings$Unit_name,
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2017_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2017_NEC_workings$NEC_n_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2017_NEC_workings$NEC_n_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2017_NEC_workings$missing_NEC_data)
 )
```

```{r, 2018 NEC}
nnap_2018_NEC_workings <-
  data.frame(
    Unit_name=
      nnap_2018_data_Necrotising_enterocolitis$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2018_data_Necrotising_enterocolitis$Count_eligible_babies_Necrotising_enterocolitis),

    NEC_n_with_NEC_data=
      as.numeric(nnap_2018_data_Necrotising_enterocolitis$With_outcome_Necrotising_enterocolitis),
    
    NEC_n_without_NEC_no=
      as.numeric(nnap_2018_data_Necrotising_enterocolitis$No_NEC_total_Necrotising_enterocolitis),
    
    NEC_n_with_NEC_yes=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Necrotising_enterocolitis$NEC_pct_Necrotising_enterocolitis)
        ),
    NEC_n_missing_NEC_data=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Necrotising_enterocolitis$Missing_pct_Necrotising_enterocolitis)
        )
)

nnap_2018_NEC <-
  data.frame(
    Unit_name=
      gsub("\\d", "", x=nnap_2018_NEC_workings$Unit_name),
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2018_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2018_NEC_workings$NEC_n_with_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2018_NEC_workings$NEC_n_without_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2018_NEC_workings$NEC_n_missing_NEC_data)
  )
```

```{r, 2019 NEC}
nnap_2019_NEC_workings <-
  data.frame(
    Unit_name=
      nnap_2019_data_NEC$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2019_data_NEC$Number_of_eligible_babies_NEC),

    NEC_n_with_NEC_data=
      as.numeric(nnap_2019_data_NEC$Number_of_eligible_babies_with_outcome_NEC),
    
    NEC_n_without_NEC_no=
        as.numeric(
          sub(" .*", "", nnap_2019_data_NEC$`No_NEC_(%_of_eligible_babies)_NEC`)
        ),
    
    NEC_n_with_NEC_yes=
        as.numeric(
          sub(" .*", "", nnap_2019_data_NEC$`NEC_(%_of_eligible_babies)_NEC`)
        ),
    NEC_n_missing_NEC_data=
        as.numeric(
          sub(" .*", "", nnap_2019_data_NEC$`Missing_Data_(%)_NEC`)
        )
)

nnap_2019_NEC <-
  data.frame(
    Unit_name=
      nnap_2019_NEC_workings$Unit_name,
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2019_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2019_NEC_workings$NEC_n_with_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2019_NEC_workings$NEC_n_without_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2019_NEC_workings$NEC_n_missing_NEC_data)
  )
```

```{r, 2020 NEC}
nnap_2020_NEC_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_NEC$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2020_data_NEC$Number_of_eligible_babies_NEC),

    NEC_n_with_NEC_data=
      as.numeric(nnap_2020_data_NEC$Number_of_eligible_babies_with_outcome_NEC),
    
    NEC_n_without_NEC_no=
        as.numeric(
          sub(" .*", "", nnap_2020_data_NEC$`No_NEC_(%_of_eligible_babies)_NEC`)
        ),
    
    NEC_n_with_NEC_yes=
        as.numeric(
          sub(" .*", "", nnap_2020_data_NEC$`NEC_(%_of_eligible_babies)_NEC`)
        ),
    NEC_n_missing_NEC_data=
        as.numeric(
          sub(" .*", "", nnap_2020_data_NEC$`Missing_Data_(%)_NEC`)
        )
)

nnap_2020_NEC <-
  data.frame(
    Unit_name=
      nnap_2020_NEC_workings$Unit_name,
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2020_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2020_NEC_workings$NEC_n_with_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2020_NEC_workings$NEC_n_without_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2020_NEC_workings$NEC_n_missing_NEC_data)
  )
```

```{r, 2021 NEC}
nnap_2021_NEC_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_NEC$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2021_data_NEC$Number_of_eligible_babies_NEC),

    NEC_n_with_NEC_data=
      as.numeric(nnap_2021_data_NEC$Number_of_eligible_babies_with_outcome_NEC),
    
    NEC_n_without_NEC_no=
        as.numeric(
          sub(" .*", "", nnap_2021_data_NEC$`No_NEC_(%_of_eligible_babies)_NEC`)
        ),
    
    NEC_n_with_NEC_yes=
        as.numeric(
          sub(" .*", "", nnap_2021_data_NEC$`NEC_(%_of_eligible_babies)_NEC`)
        ),
    NEC_n_missing_NEC_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_NEC$`Missing_Data_(%)_NEC`)
        )
)

nnap_2021_NEC <-
  data.frame(
    Unit_name=
      nnap_2021_NEC_workings$Unit_name,
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2021_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2021_NEC_workings$NEC_n_with_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2021_NEC_workings$NEC_n_without_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2021_NEC_workings$NEC_n_missing_NEC_data)
  )
```

```{r, 2022 NEC}
nnap_2022_NEC_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_NEC$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2022_data_0_NEC$NumberOfEligibleBabies_NEC),

    NEC_n_with_NEC_data=
      as.numeric(nnap_2022_data_0_NEC$Outcome_NEC),
    
    NEC_n_without_NEC_no=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_NEC$NoNecCombined_NEC)
        ),
    
    NEC_n_with_NEC_yes=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_NEC$Nec_NEC)
        ),
    NEC_n_missing_NEC_data=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_NEC$MissingTotal_NEC)
        )
)

nnap_2022_NEC_workings <-
  nnap_2022_NEC_workings %>%
  filter(Unit_name!="ALLPARTICIPATINGUNITS") %>%
  filter(!is.na(Unit_name))

nnap_2022_NEC <-
  data.frame(
    Unit_name=
      nnap_2022_NEC_workings$Unit_name,
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2022_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2022_NEC_workings$NEC_n_with_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2022_NEC_workings$NEC_n_without_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2022_NEC_workings$NEC_n_missing_NEC_data)
  )
```

```{r, 2023 NEC}
nnap_2023_NEC_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_NEC$Unit_name,
    NEC_n_eligible=
      as.numeric(nnap_2023_data_masked_NEC$Eligible_NEC),

    NEC_n_with_NEC_data=
      as.numeric(nnap_2023_data_masked_NEC$With_outcome_NEC),
    
    NEC_n_without_NEC_and_died=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_NEC$`No_NEC_-_died_NEC`)
        ),
    NEC_n_without_NEC_and_alive=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_NEC$`No_NEC_-_Alive_NEC`)
        ),
    
    NEC_n_with_NEC_yes=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_NEC$NEC_NEC)
        ),
    NEC_n_missing_NEC_data=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_NEC$Missing_NEC)
        )
)

nnap_2023_NEC_workings$NEC_n_without_NEC_no <- 
  nnap_2023_NEC_workings$NEC_n_without_NEC_and_died + 
  nnap_2023_NEC_workings$NEC_n_without_NEC_and_alive

nnap_2023_NEC <-
  data.frame(
    Unit_name=
      nnap_2023_NEC_workings$Unit_name,
    NEC_n_alive_and_dead_eligible=
      as.numeric(nnap_2023_NEC_workings$NEC_n_eligible),
    NEC_n_yes_NEC=
      as.numeric(nnap_2023_NEC_workings$NEC_n_with_NEC_yes),
    NEC_n_no_NEC=
      as.numeric(nnap_2023_NEC_workings$NEC_n_without_NEC_no),
    NEC_n_missing_NEC_data=
      as.numeric(nnap_2023_NEC_workings$NEC_n_missing_NEC_data)
  )
```

**************************
Extract the sepsis data for each year
**************************

```{r, 2017 sepsis}
nnap_2017_data_0_Bloodstream_infection_less_than_32 <-
  subset(nnap_2017_data_0_Bloodstream_infection, Gestation_weeks_Bloodstream_infection=="< 32 weeks")
nnap_2017_data_0_Bloodstream_infection_greater_equal_32 <-
  subset(nnap_2017_data_0_Bloodstream_infection, Gestation_weeks_Bloodstream_infection==">= 32 weeks")

nnap_2017_sepsis_workings <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Bloodstream_infection_less_than_32$Unit_name,
    
    sepsis_n_eligible_less_than_32=
      as.numeric(nnap_2017_data_0_Bloodstream_infection_less_than_32$Number_of_babies_admitted_Bloodstream_infection),
    
    sepsis_n_with_sepsis_less_than_32_yes=
      as.numeric(nnap_2017_data_0_Bloodstream_infection_less_than_32$Babies_with_one_or_more_pure_growths_of_a_pathogen_Bloodstream_infection),
    
    Unit_name_check=
      nnap_2017_data_0_Bloodstream_infection_greater_equal_32$Unit_name,
    
    sepsis_n_eligible_greater_than_32=
      as.numeric(nnap_2017_data_0_Bloodstream_infection_greater_equal_32$Number_of_babies_admitted_Bloodstream_infection),
    
    sepsis_n_with_sepsis_greater_than_32_yes=
      as.numeric(nnap_2017_data_0_Bloodstream_infection_greater_equal_32$Babies_with_one_or_more_pure_growths_of_a_pathogen_Bloodstream_infection)
    
    
)

nnap_2017_sepsis_workings$sepsis_n_eligible <- 
  as.numeric(nnap_2017_sepsis_workings$sepsis_n_eligible_less_than_32) +
  as.numeric(nnap_2017_sepsis_workings$sepsis_n_eligible_greater_than_32)

nnap_2017_sepsis_workings$sepsis_n_with_sepsis_yes <- 
  as.numeric(nnap_2017_sepsis_workings$sepsis_n_with_sepsis_less_than_32_yes) +
  as.numeric(nnap_2017_sepsis_workings$sepsis_n_with_sepsis_greater_than_32_yes)

nnap_2017_sepsis_workings$sepsis_n_without_sepsis_no <- 
  nnap_2017_sepsis_workings$sepsis_n_eligible - 
  nnap_2017_sepsis_workings$sepsis_n_with_sepsis_yes

nnap_2017_sepsis <-
  data.frame(
    Unit_name=
      nnap_2017_sepsis_workings$Unit_name,
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2017_sepsis_workings$sepsis_n_eligible),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2017_sepsis_workings$sepsis_n_with_sepsis_yes),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2017_sepsis_workings$sepsis_n_without_sepsis_no),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA)
  )
```

```{r, 2018 sepsis}
nnap_2018_data_Bloodstream_infection_total <- 
  subset(nnap_2018_data_Bloodstream_infection, Gestation_weeks_Bloodstream_infection=="Total") 

nnap_2018_sepsis_workings <-
  data.frame(
    Unit_name=
      nnap_2018_data_Bloodstream_infection_total$Unit_name,
    
    sepsis_n_eligible_total=
      as.numeric(nnap_2018_data_Bloodstream_infection_total$CountbBaby_Bloodstream_infection),
    
    sepsis_n_with_sepsis_total=
      as.numeric(nnap_2018_data_Bloodstream_infection_total$unique_pure_growth_pathogen_Bloodstream_infection)
    )

nnap_2018_sepsis_workings$sepsis_n_without_sepsis_total <- 
  nnap_2018_sepsis_workings$sepsis_n_eligible_total - 
  nnap_2018_sepsis_workings$sepsis_n_with_sepsis_total

nnap_2018_sepsis <-
  data.frame(
    Unit_name=
      gsub("\\d", "", x=nnap_2018_sepsis_workings$Unit_name),
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2018_sepsis_workings$sepsis_n_eligible_total),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2018_sepsis_workings$sepsis_n_with_sepsis_total),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2018_sepsis_workings$sepsis_n_without_sepsis_total),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA) 
  )
```

```{r, 2019 sepsis}
nnap_2019_sepsis_workings <-
  data.frame(
    Unit_name=
      nnap_2019_data_BSI$Unit_name,
    
    sepsis_n_eligible_less_than_32=
      as.numeric(nnap_2019_data_BSI$Number_of_babies_admitted_less_than_32_weeks_gestation_BSI),
    
    sepsis_n_with_sepsis_less_than_32_yes=
      as.numeric(
        sub(" .*", "", nnap_2019_data_BSI$Number_of_babies_with_one_or_more_growths_of_a_clearly_pathogenic_organism_less_than_32_weeks_gestation_BSI)
        ),

    sepsis_n_eligible_greater_than_32=
       as.numeric(nnap_2019_data_BSI$Number_of_babies_admitted_greater_than_32_weeks_gestation_BSI),
    
    sepsis_n_with_sepsis_greater_than_32_yes=
      as.numeric(
        sub(" .*", "", nnap_2019_data_BSI$Number_of_babies_with_one_or_more_growths_of_a_clearly_pathogenic_organism_greater_than_32_weeks_gestation_BSI)
        )
    )

nnap_2019_sepsis_workings$sepsis_n_eligible <- 
  as.numeric(nnap_2019_sepsis_workings$sepsis_n_eligible_less_than_32) +
  as.numeric(nnap_2019_sepsis_workings$sepsis_n_eligible_greater_than_32)

nnap_2019_sepsis_workings$sepsis_n_with_sepsis_yes <- 
  as.numeric(nnap_2019_sepsis_workings$sepsis_n_with_sepsis_less_than_32_yes) +
  as.numeric(nnap_2019_sepsis_workings$sepsis_n_with_sepsis_greater_than_32_yes)

nnap_2019_sepsis_workings$sepsis_n_without_sepsis_no <- 
  nnap_2019_sepsis_workings$sepsis_n_eligible - 
  nnap_2019_sepsis_workings$sepsis_n_with_sepsis_yes

nnap_2019_sepsis <-
  data.frame(
    Unit_name=
      nnap_2019_sepsis_workings$Unit_name,
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2019_sepsis_workings$sepsis_n_eligible),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2019_sepsis_workings$sepsis_n_with_sepsis_yes),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2019_sepsis_workings$sepsis_n_without_sepsis_no),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA)
  )
```

```{r, 2020 sepsis}

nnap_2020_sepsis_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_Bloodstream_infection$Unit_name,
    
    sepsis_n_eligible_less_than_32=
      as.numeric(nnap_2020_data_Bloodstream_infection$Number_of_babies_admitted_Less_than_32_weeks_gestation_at_birth_Bloodstream_infection),
    
    sepsis_n_with_sepsis_less_than_32_yes=
      as.numeric(
        sub(" .*", "", nnap_2020_data_Bloodstream_infection$Number_of_babies_with_one_or_more_growths_of_a_clearly_pathogenic_organism_Less_than_32_weeks_gestation_at_birth_Bloodstream_infection)
        ),

    sepsis_n_eligible_greater_than_32=
       as.numeric(nnap_2020_data_Bloodstream_infection$Number_of_admissions_Greater_than_or_equal_to_32_weeks_gestation_at_birth_Bloodstream_infection),
    
    sepsis_n_with_sepsis_greater_than_32_yes=
      as.numeric(
        sub(" .*", "", nnap_2020_data_Bloodstream_infection$Number_of_babies_with_one_or_more_growths_of_a_clearly_pathogenic_organism_Greater_than_or_equal_to_32_weeks_gestation_at_birth_Bloodstream_infection)
        )
    )

nnap_2020_sepsis_workings$sepsis_n_eligible <- 
  as.numeric(nnap_2020_sepsis_workings$sepsis_n_eligible_less_than_32) +
  as.numeric(nnap_2020_sepsis_workings$sepsis_n_eligible_greater_than_32)

nnap_2020_sepsis_workings$sepsis_n_with_sepsis_yes <- 
  as.numeric(nnap_2020_sepsis_workings$sepsis_n_with_sepsis_less_than_32_yes) +
  as.numeric(nnap_2020_sepsis_workings$sepsis_n_with_sepsis_greater_than_32_yes)

nnap_2020_sepsis_workings$sepsis_n_without_sepsis_no <- 
  nnap_2020_sepsis_workings$sepsis_n_eligible - 
  nnap_2020_sepsis_workings$sepsis_n_with_sepsis_yes

nnap_2020_sepsis <-
  data.frame(
    Unit_name=
      nnap_2020_sepsis_workings$Unit_name,
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2020_sepsis_workings$sepsis_n_eligible),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2020_sepsis_workings$sepsis_n_with_sepsis_yes),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2020_sepsis_workings$sepsis_n_without_sepsis_no),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA) 
  )
```

```{r, 2021 sepsis}
nnap_2021_sepsis_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_BSI$Unit_name,
    
    sepsis_n_eligible_less_than_32=
      as.numeric(nnap_2021_data_BSI$Number_of_babies_admitted_Less_than_32_weeks_gestation_at_birth_BSI),
    
    sepsis_n_with_sepsis_less_than_32_yes=
      as.numeric(
        sub(" .*", "", nnap_2021_data_BSI$Number_of_babies_with_one_or_more_growths_of_a_clearly_pathogenic_organism...6_BSI)
        ),

    sepsis_n_eligible_greater_than_32=
       as.numeric(nnap_2021_data_BSI$Number_of_babies_admitted_Greater_than_or_equal_to_32_weeks_gestation_at_birth_BSI),
    
    sepsis_n_with_sepsis_greater_than_32_yes=
      as.numeric(
        sub(" .*", "", nnap_2021_data_BSI$Number_of_babies_with_one_or_more_growths_of_a_clearly_pathogenic_organism...10_BSI)
        )
    )

nnap_2021_sepsis_workings$sepsis_n_eligible <- 
  as.numeric(nnap_2021_sepsis_workings$sepsis_n_eligible_less_than_32) +
  as.numeric(nnap_2021_sepsis_workings$sepsis_n_eligible_greater_than_32)

nnap_2021_sepsis_workings$sepsis_n_with_sepsis_yes <- 
  as.numeric(nnap_2021_sepsis_workings$sepsis_n_with_sepsis_less_than_32_yes) +
  as.numeric(nnap_2021_sepsis_workings$sepsis_n_with_sepsis_greater_than_32_yes)

nnap_2021_sepsis_workings$sepsis_n_without_sepsis_no <- 
  nnap_2021_sepsis_workings$sepsis_n_eligible - 
  nnap_2021_sepsis_workings$sepsis_n_with_sepsis_yes

nnap_2021_sepsis <-
  data.frame(
    Unit_name=
      nnap_2021_sepsis_workings$Unit_name,
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2021_sepsis_workings$sepsis_n_eligible),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2021_sepsis_workings$sepsis_n_with_sepsis_yes),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2021_sepsis_workings$sepsis_n_without_sepsis_no),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA)
  )
```

```{r, 2022 sepsis}
nnap_2022_sepsis_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_BSI$Unit_name,
    
    sepsis_n_eligible_less_than_32=
      as.numeric(nnap_2022_data_0_BSI$BabiesAdmittedLT32_BSI),
    
    sepsis_n_with_sepsis_less_than_32_yes=
        as.numeric(nnap_2022_data_0_BSI$PurePathogensLT32_BSI),
    
    sepsis_n_eligible_greater_than_32=
      as.numeric(nnap_2022_data_0_BSI$BabiesAdmittedGT32_BSI),
    
    sepsis_n_with_sepsis_greater_than_32_yes=
        as.numeric(nnap_2022_data_0_BSI$PurePathogensGT32_BSI)
    )

nnap_2022_sepsis_workings$sepsis_n_eligible <- 
  as.numeric(nnap_2022_sepsis_workings$sepsis_n_eligible_less_than_32) +
  as.numeric(nnap_2022_sepsis_workings$sepsis_n_eligible_greater_than_32)

nnap_2022_sepsis_workings$sepsis_n_with_sepsis_yes <- 
  as.numeric(nnap_2022_sepsis_workings$sepsis_n_with_sepsis_less_than_32_yes) +
  as.numeric(nnap_2022_sepsis_workings$sepsis_n_with_sepsis_greater_than_32_yes)

nnap_2022_sepsis_workings$sepsis_n_without_sepsis_no <- 
  nnap_2022_sepsis_workings$sepsis_n_eligible - 
  nnap_2022_sepsis_workings$sepsis_n_with_sepsis_yes

nnap_2022_sepsis <-
  data.frame(
    Unit_name=
      nnap_2022_sepsis_workings$Unit_name,
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2022_sepsis_workings$sepsis_n_eligible),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2022_sepsis_workings$sepsis_n_with_sepsis_yes),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2022_sepsis_workings$sepsis_n_without_sepsis_no),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA)
  )
```

```{r, 2023 sepsis}
nnap_2023_data_masked_BSI_totals <- 
  subset(nnap_2023_data_masked_BSI, Gestation_in_Weeks_BSI==".") 

nnap_2023_sepsis_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_BSI_totals$Unit_name,
    
    sepsis_n_eligible=
      as.numeric(nnap_2023_data_masked_BSI_totals$Babies_in_units_BSI),
    
    sepsis_n_with_sepsis_yes=
        as.numeric(
          nnap_2023_data_masked_BSI_totals$Unique_pathogen_BSI
        )
    )

nnap_2023_sepsis_workings$sepsis_n_without_sepsis_no <- 
  as.numeric(nnap_2023_sepsis_workings$sepsis_n_eligible) - 
  as.numeric(nnap_2023_sepsis_workings$sepsis_n_with_sepsis_yes)

nnap_2023_sepsis <-
  data.frame(
    Unit_name=
      nnap_2023_sepsis_workings$Unit_name,
    sepsis_n_alive_and_dead_eligible=
      as.numeric(nnap_2023_sepsis_workings$sepsis_n_eligible),
    sepsis_n_yes_sepsis=
      as.numeric(nnap_2023_sepsis_workings$sepsis_n_with_sepsis_yes),
    sepsis_n_no_sepsis=
      as.numeric(nnap_2023_sepsis_workings$sepsis_n_without_sepsis_no),
    sepsis_n_missing_sepsis_data=
      as.numeric(NA) 
  )
```

**************************
Extract the cPVL data for each year
**************************

cPVL after they started collecting was always defined by grade 3 or grade 4, limited because it needs cranial ultrasounds to be entered into badger

cPVL first year of data collection was 2021, so all previous years are NA

```{r, 2017 to 2020 cPVL are all created as NA}
nnap_2017_cPVL <-
  data.frame(
    Unit_name=nnap_2017_data_0_Bronchopulmonary_dysplasia$Unit_name,
    cPVL_n_alive_and_dead_eligible=as.numeric(NA),
    cPVL_n_yes_cPVL=as.numeric(NA),
    cPVL_n_no_cPVL=as.numeric(NA),
    cPVL_n_missing_cPVL_data=as.numeric(NA)
  )

nnap_2018_cPVL <-
  data.frame(
    Unit_name=gsub("\\d", "", x=nnap_2018_data_Bronchopulmonary_dysplasia$Unit_name),
    cPVL_n_alive_and_dead_eligible=as.numeric(NA),
    cPVL_n_yes_cPVL=as.numeric(NA),
    cPVL_n_no_cPVL=as.numeric(NA),
    cPVL_n_missing_cPVL_data=as.numeric(NA)
  )

nnap_2019_cPVL <-
  data.frame(
    Unit_name=nnap_2019_data_BPD$Unit_name,
    cPVL_n_alive_and_dead_eligible=as.numeric(NA),
    cPVL_n_yes_cPVL=as.numeric(NA),
    cPVL_n_no_cPVL=as.numeric(NA),
    cPVL_n_missing_cPVL_data=as.numeric(NA)
  )

nnap_2020_cPVL <-
  data.frame(
    Unit_name=nnap_2020_data_BPD$Unit_name,
    cPVL_n_alive_and_dead_eligible=as.numeric(NA),
    cPVL_n_yes_cPVL=as.numeric(NA),
    cPVL_n_no_cPVL=as.numeric(NA),
    cPVL_n_missing_cPVL_data=as.numeric(NA)
  )
```

```{r, 2021 cPVL}
nnap_2021_cPVL_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_cPVL$Unit_name,
    
    cPVL_n_eligible=
      as.numeric(nnap_2021_data_cPVL$Number_Of_Eligible_Babies_cPVL),

    cPVL_n_with_cPVL_data=
      as.numeric(nnap_2021_data_cPVL$Babies_With_Outcome_cPVL),
    
    cPVL_n_with_cPVL_yes=
        as.numeric(
          nnap_2021_data_cPVL$cPVL_cPVL
        ),
    cPVL_n_missing_cPVL_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_cPVL$`Missing_(%)_cPVL`)
        )
)
nnap_2021_cPVL_workings$cPVL_n_without_cPVL_no <-
  nnap_2021_cPVL_workings$cPVL_n_with_cPVL_data - nnap_2021_cPVL_workings$cPVL_n_with_cPVL_yes

nnap_2021_cPVL <-
  data.frame(
    Unit_name=
      nnap_2021_cPVL_workings$Unit_name,
    cPVL_n_alive_and_dead_eligible=
      as.numeric(nnap_2021_cPVL_workings$cPVL_n_eligible),
    cPVL_n_yes_cPVL=
      as.numeric(nnap_2021_cPVL_workings$cPVL_n_with_cPVL_yes),
    cPVL_n_no_cPVL=
      as.numeric(nnap_2021_cPVL_workings$cPVL_n_without_cPVL_no),
    cPVL_n_missing_cPVL_data=
      as.numeric(nnap_2021_cPVL_workings$cPVL_n_missing_cPVL_data)
  )
```

```{r, 2022 cPVL}
nnap_2022_cPVL_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_cPVL$Unit_name,
    
    cPVL_n_eligible=
      as.numeric(nnap_2022_data_0_cPVL$cPVLEligibleBabies_cPVL),

    cPVL_n_with_cPVL_data=
      as.numeric(nnap_2022_data_0_cPVL$cPVLOutcome_cPVL),
    
    cPVL_n_with_cPVL_yes=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_cPVL$cPVL_cPVL)
        ),
    cPVL_n_missing_cPVL_data=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_cPVL$cPVLMissing_cPVL)
        )
)

nnap_2022_cPVL_workings$cPVL_n_without_cPVL_no <-
  nnap_2022_cPVL_workings$cPVL_n_with_cPVL_data -
  nnap_2022_cPVL_workings$cPVL_n_with_cPVL_yes 

nnap_2022_cPVL_workings <-
  nnap_2022_cPVL_workings %>%
  filter(Unit_name!="ALLPARTICIPATINGUNITS") %>%
  filter(!is.na(Unit_name))

nnap_2022_cPVL <-
  data.frame(
    Unit_name=
      nnap_2022_cPVL_workings$Unit_name,
    cPVL_n_alive_and_dead_eligible=
      as.numeric(nnap_2022_cPVL_workings$cPVL_n_eligible),
    cPVL_n_yes_cPVL=
      as.numeric(nnap_2022_cPVL_workings$cPVL_n_with_cPVL_yes),
    cPVL_n_no_cPVL=
      as.numeric(nnap_2022_cPVL_workings$cPVL_n_without_cPVL_no),
    cPVL_n_missing_cPVL_data=
      as.numeric(nnap_2022_cPVL_workings$cPVL_n_missing_cPVL_data)
  )
```

```{r, 2023 cPVL}
nnap_2023_cPVL_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_cPVL$Unit_name,
    cPVL_n_eligible=
      as.numeric(nnap_2023_data_masked_cPVL$Eligible_cPVL),

    cPVL_n_with_cPVL_data=
      as.numeric(nnap_2023_data_masked_cPVL$cPVL_Outcome_cPVL),
    
    cPVL_n_with_cPVL_3_or_4_and_died=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_cPVL$cPVL_Died_cPVL)
        ),
    cPVL_n_with_cPVL_3_or_4_and_alive=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_cPVL$cPVL_Alive_cPVL)
        ),
    
    cPVL_n_missing_cPVL_data=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_cPVL$Missing_cPVL)
        )
)

nnap_2023_cPVL_workings$cPVL_n_with_cPVL_3_or_4_dead_or_alive <- 
  nnap_2023_cPVL_workings$cPVL_n_with_cPVL_3_or_4_and_died + 
  nnap_2023_cPVL_workings$cPVL_n_with_cPVL_3_or_4_and_alive
nnap_2023_cPVL_workings$cPVL_n_without_cPVL_3_or_4_dead_or_alive <- 
  nnap_2023_cPVL_workings$cPVL_n_with_cPVL_data - 
  nnap_2023_cPVL_workings$cPVL_n_with_cPVL_3_or_4_dead_or_alive


nnap_2023_cPVL <-
  data.frame(
    Unit_name=
      nnap_2023_cPVL_workings$Unit_name,
    cPVL_n_alive_and_dead_eligible=
      as.numeric(nnap_2023_cPVL_workings$cPVL_n_eligible),
    cPVL_n_yes_cPVL=
      as.numeric(nnap_2023_cPVL_workings$cPVL_n_with_cPVL_3_or_4_dead_or_alive),
    cPVL_n_no_cPVL=
      as.numeric(nnap_2023_cPVL_workings$cPVL_n_without_cPVL_3_or_4_dead_or_alive),
    cPVL_n_missing_cPVL_data=
      as.numeric(nnap_2023_cPVL_workings$cPVL_n_missing_cPVL_data)
  )

```

**************************
Extract the IVH data for each year
**************************

IVH first year of data collection was 2021, so all previous years are NA

```{r, 2017 to 2020 IVH are all created as NA}
nnap_2017_IVH <-
  data.frame(
    Unit_name=nnap_2017_data_0_Bronchopulmonary_dysplasia$Unit_name,
    IVH_n_alive_and_dead_eligible=as.numeric(NA),
    IVH_n_yes_IVH=as.numeric(NA),
    IVH_n_no_IVH=as.numeric(NA),
    IVH_n_missing_IVH_data=as.numeric(NA)
  )

nnap_2018_IVH <-
  data.frame(
    Unit_name=gsub("\\d", "", x=nnap_2018_data_Bronchopulmonary_dysplasia$Unit_name),
    IVH_n_alive_and_dead_eligible=as.numeric(NA),
    IVH_n_yes_IVH=as.numeric(NA),
    IVH_n_no_IVH=as.numeric(NA),
    IVH_n_missing_IVH_data=as.numeric(NA)
  )

nnap_2019_IVH <-
  data.frame(
    Unit_name=nnap_2019_data_BPD$Unit_name,
    IVH_n_alive_and_dead_eligible=as.numeric(NA),
    IVH_n_yes_IVH=as.numeric(NA),
    IVH_n_no_IVH=as.numeric(NA),
    IVH_n_missing_IVH_data=as.numeric(NA)
  )

nnap_2020_IVH <-
  data.frame(
    Unit_name=nnap_2020_data_BPD$Unit_name,
    IVH_n_alive_and_dead_eligible=as.numeric(NA),
    IVH_n_yes_IVH=as.numeric(NA),
    IVH_n_no_IVH=as.numeric(NA),
    IVH_n_missing_IVH_data=as.numeric(NA)
  )
```

```{r, 2021 IVH}
nnap_2021_IVH_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_IVH$Unit_name,
    
    IVH_n_eligible=
      as.numeric(nnap_2021_data_IVH$Number_Of_Eligible_Babies_IVH),

    IVH_n_with_IVH_data=
      as.numeric(nnap_2021_data_IVH$Babies_With_Outcome_IVH),
    
    IVH_n_with_IVH_yes=
        as.numeric(
          nnap_2021_data_IVH$IVH34_IVH
        ),
    IVH_n_missing_IVH_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_IVH$`Missing_(%)_IVH`)
        )
)
nnap_2021_IVH_workings$IVH_n_without_IVH_no <-
  nnap_2021_IVH_workings$IVH_n_with_IVH_data - nnap_2021_IVH_workings$IVH_n_with_IVH_yes

nnap_2021_IVH <-
  data.frame(
    Unit_name=
      nnap_2021_IVH_workings$Unit_name,
    IVH_n_alive_and_dead_eligible=
      as.numeric(nnap_2021_IVH_workings$IVH_n_eligible),
    IVH_n_yes_IVH=
      as.numeric(nnap_2021_IVH_workings$IVH_n_with_IVH_yes),
    IVH_n_no_IVH=
      as.numeric(nnap_2021_IVH_workings$IVH_n_without_IVH_no),
    IVH_n_missing_IVH_data=
      as.numeric(nnap_2021_IVH_workings$IVH_n_missing_IVH_data)
  )
```

```{r, 2022 IVH}
nnap_2022_IVH_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_IVH$Unit_name,
    
    IVH_n_eligible=
      as.numeric(nnap_2022_data_0_IVH$IVHEligibleBabies_IVH),

    IVH_n_with_IVH_data=
      as.numeric(nnap_2022_data_0_IVH$IVHOutcome_IVH),
    
    IVH_n_with_IVH_yes=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_IVH$IVH34_IVH)
        ),
    IVH_n_missing_IVH_data=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_IVH$IVHMissing_IVH)
        )
)

nnap_2022_IVH_workings$IVH_n_without_IVH_no <-
  nnap_2022_IVH_workings$IVH_n_with_IVH_data -
  nnap_2022_IVH_workings$IVH_n_with_IVH_yes 

nnap_2022_IVH_workings <-
  nnap_2022_IVH_workings %>%
  filter(Unit_name!="ALLPARTICIPATINGUNITS") %>%
  filter(!is.na(Unit_name))

nnap_2022_IVH <-
  data.frame(
    Unit_name=
      nnap_2022_IVH_workings$Unit_name,
    IVH_n_alive_and_dead_eligible=
      as.numeric(nnap_2022_IVH_workings$IVH_n_eligible),
    IVH_n_yes_IVH=
      as.numeric(nnap_2022_IVH_workings$IVH_n_with_IVH_yes),
    IVH_n_no_IVH=
      as.numeric(nnap_2022_IVH_workings$IVH_n_without_IVH_no),
    IVH_n_missing_IVH_data=
      as.numeric(nnap_2022_IVH_workings$IVH_n_missing_IVH_data)
  )
```

```{r, 2023 IVH}
nnap_2023_IVH_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_IVH$Unit_name,
    IVH_n_eligible=
      as.numeric(nnap_2023_data_masked_IVH$Eligible_IVH),

    IVH_n_with_IVH_data=
      as.numeric(nnap_2023_data_masked_IVH$IVH_outcome_IVH),
    
    IVH_n_with_IVH_3_or_4_and_died=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_IVH$`IVH3/4_-_Died_IVH`)
        ),
    IVH_n_with_IVH_3_or_4_and_alive=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_IVH$`IVH3/4_-_Alive_IVH`)
        ),
    
    IVH_n_missing_IVH_data=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_IVH$Missing_data_IVH)
        )
)

nnap_2023_IVH_workings$IVH_n_with_IVH_3_or_4_dead_or_alive <- 
  nnap_2023_IVH_workings$IVH_n_with_IVH_3_or_4_and_died + 
  nnap_2023_IVH_workings$IVH_n_with_IVH_3_or_4_and_alive

nnap_2023_IVH_workings$IVH_n_without_IVH_3_or_4_dead_or_alive <- 
  nnap_2023_IVH_workings$IVH_n_with_IVH_data - 
  nnap_2023_IVH_workings$IVH_n_with_IVH_3_or_4_dead_or_alive

nnap_2023_IVH <-
  data.frame(
    Unit_name=
      nnap_2023_IVH_workings$Unit_name,
    IVH_n_alive_and_dead_eligible=
      as.numeric(nnap_2023_IVH_workings$IVH_n_eligible),
    IVH_n_yes_IVH=
      as.numeric(nnap_2023_IVH_workings$IVH_n_with_IVH_3_or_4_dead_or_alive),
    IVH_n_no_IVH=
      as.numeric(nnap_2023_IVH_workings$IVH_n_without_IVH_3_or_4_dead_or_alive),
    IVH_n_missing_IVH_data=
      as.numeric(nnap_2023_IVH_workings$IVH_n_missing_IVH_data)
  )

```

******************************************************************************************
temperature at admission normothermia
******************************************************************************************

```{r, 2017 Temperature}
nnap_2017_Temperature_workings <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Temperature$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2017_data_0_Temperature$Eligible_babies_Temperature),
    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2017_data_0_Temperature$With_outcome_Temperature),

    Temperature_n_normothermia_yes=
      as.numeric(nnap_2017_data_0_Temperature$`Temp._36.5_to_37.5°C_number_Temperature`),
    
    Temperature_n_Temperature_low=
      as.numeric(
        nnap_2017_data_0_Temperature$`Temp._less_than_32°C_Temperature` +
        nnap_2017_data_0_Temperature$`Temp._32_to_35.9°C_Temperature` +
        nnap_2017_data_0_Temperature$`Temp._36_to_36.4°C_number_Temperature` 
        ),
    
    Temperature_n_Temperature_high=
      as.numeric(
        nnap_2017_data_0_Temperature$`Temp._greater_than_37.5°C_number_Temperature`
        )
)

nnap_2017_Temperature_workings$Temperature_n_Temperature_missing <-
  nnap_2017_data_0_Temperature$Not_taken_Temperature +
  nnap_2017_data_0_Temperature$After_hour_Temperature +
  nnap_2017_data_0_Temperature$Missing_data_number_Temperature

nnap_2017_Temperature_workings$Temperature_n_normothermia_no <-
  as.numeric(nnap_2017_Temperature_workings$Temperature_n_Temperature_low) +
  as.numeric(nnap_2017_Temperature_workings$Temperature_n_Temperature_high)

nnap_2017_Temperature <-
  data.frame(
    Unit_name=
      nnap_2017_Temperature_workings$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2017_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2017_Temperature_workings$Temperature_n_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2017_Temperature_workings$Temperature_n_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2017_Temperature_workings$Temperature_n_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2017_Temperature_workings$Temperature_n_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2017_Temperature_workings$Temperature_n_Temperature_missing)
 )
```

```{r, 2018 Temperature}
nnap_2018_Temperature_workings <-
  data.frame(
    Unit_name=
      nnap_2018_data_Temperature$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2018_data_Temperature$Count_eligible_babies_Temperature),

    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2018_data_Temperature$With_outcome_Temperature),
    
    Temperature_n_with_Temperature_low=
      as.numeric(nnap_2018_data_Temperature$lessthan32_Temperature) +
      as.numeric(nnap_2018_data_Temperature$`32-35.9_Temperature`) +
      as.numeric(
        sub(" .*", "", (nnap_2018_data_Temperature$`36-36.4_Temperature`))),
    
    Temperature_n_with_Temperature_high=
      as.numeric(
        sub(" .*", "", (nnap_2018_data_Temperature$morethan_37.5_Temperature))),
    
    Temperature_n_with_normothermia_yes=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Temperature$`36.5-37.5_Temperature`)
        ),
    Temperature_n_missing_Temperature_data=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Temperature$Missing_data_Temperature)
        ) +
      as.numeric(
          sub(" .*", "", nnap_2018_data_Temperature$After_hour_Temperature)
        ) +
      as.numeric(
          sub(" .*", "", nnap_2018_data_Temperature$Not_taken_Temperature)
        )
)

nnap_2018_Temperature_workings$Temperature_n_with_normothermia_no <-
  as.numeric(nnap_2018_Temperature_workings$Temperature_n_with_Temperature_low) + 
  as.numeric(nnap_2018_Temperature_workings$Temperature_n_with_Temperature_high)

nnap_2018_Temperature <-
  data.frame(
    Unit_name=
      gsub("\\d", "", x=nnap_2018_Temperature_workings$Unit_name),
    Temperature_n_eligible=
      as.numeric(nnap_2018_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2018_Temperature_workings$Temperature_n_with_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2018_Temperature_workings$Temperature_n_with_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2018_Temperature_workings$Temperature_n_with_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2018_Temperature_workings$Temperature_n_with_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2018_Temperature_workings$Temperature_n_missing_Temperature_data)
  )
```

```{r, 2019 Temperature}
nnap_2019_Temperature_workings <-
  data.frame(
    Unit_name=
      nnap_2019_data_Temperature$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2019_data_Temperature$Number_of_eligible_babies_Temperature),

    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2019_data_Temperature$Number_of_eligible_babies_with_outcome_Temperature),
    
    Temperature_n_with_Temperature_low=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Temperature$`<_32°C_Temperature`)
        ) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$`32°C-35.9°C_Temperature`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$`36°C-36.4°C_Temperature`)))) ,
    
    Temperature_n_with_Temperature_high=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$`>_37.5°C_Temperature`)))) ,
    Temperature_n_with_normothermia_yes=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$`36.5°C-37.5°C_Temperature`)))),
    Temperature_n_missing_Temperature_data=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$`Missing_data_(%)_Temperature`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$Late_Temperature)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2019_data_Temperature$Not_taken_Temperature))))
)

nnap_2019_Temperature_workings$Temperature_n_with_normothermia_no <-
  as.numeric(nnap_2019_Temperature_workings$Temperature_n_with_Temperature_low) + 
  as.numeric(nnap_2019_Temperature_workings$Temperature_n_with_Temperature_high)

nnap_2019_Temperature <-
  data.frame(
    Unit_name=
      nnap_2019_Temperature_workings$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2019_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2019_Temperature_workings$Temperature_n_with_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2019_Temperature_workings$Temperature_n_with_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2019_Temperature_workings$Temperature_n_with_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2019_Temperature_workings$Temperature_n_with_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2019_Temperature_workings$Temperature_n_missing_Temperature_data)
  )
```

```{r, 2020 Temperature}
nnap_2020_Temperature_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_Temperature$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2020_data_Temperature$Number_of_eligible_babies_Temperature),

    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2020_data_Temperature$Number_of_eligible_babies_with_outcome_Temperature),
    
    Temperature_n_with_Temperature_low=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Temperature$`<_32°C_Temperature`)
        ) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$`32°C-35.9°C_Temperature`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$`36°C-36.4°C_Temperature`)))) ,
    
    Temperature_n_with_Temperature_high=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$`>_37.5°C_Temperature`)))) ,
    Temperature_n_with_normothermia_yes=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$`36.5°C-37.5°C_Temperature`)))),
    Temperature_n_missing_Temperature_data=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$`Missing_data_(%)_Temperature`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$Late_Temperature)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2020_data_Temperature$Not_taken_Temperature))))
)

nnap_2020_Temperature_workings$Temperature_n_with_normothermia_no <-
  as.numeric(nnap_2020_Temperature_workings$Temperature_n_with_Temperature_low) + 
  as.numeric(nnap_2020_Temperature_workings$Temperature_n_with_Temperature_high)

nnap_2020_Temperature <-
  data.frame(
    Unit_name=
      nnap_2020_Temperature_workings$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2020_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2020_Temperature_workings$Temperature_n_with_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2020_Temperature_workings$Temperature_n_with_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2020_Temperature_workings$Temperature_n_with_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2020_Temperature_workings$Temperature_n_with_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2020_Temperature_workings$Temperature_n_missing_Temperature_data)
  )
```

```{r, 2021 Temperature}
nnap_2021_Temperature_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_Temperature$Unit_name,
    
    Temperature_n_eligible=
      as.numeric(nnap_2021_data_Temperature$Number_of_eligible_babies_Temperature),

    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2021_data_Temperature$Number_of_eligible_babies_with_outcome_Temperature),
    
    Temperature_n_with_Temperature_low=
        as.numeric(
          sub(" .*", "", nnap_2021_data_Temperature$`<_32°C_Temperature`)
        ) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$`32°C-35.9°C_Temperature`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$`36°C-36.4°C_Temperature`)))) ,
    
    Temperature_n_with_Temperature_high=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$`>_37.5°C_Temperature`)))) ,
    Temperature_n_with_normothermia_yes=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$`36.5°C-37.5°C_Temperature`)))),
    Temperature_n_missing_Temperature_data=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$`Missing_data_(%)_Temperature`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$Late_Temperature)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2021_data_Temperature$Not_taken_Temperature))))
)

nnap_2021_Temperature_workings$Temperature_n_with_normothermia_no <-
  as.numeric(nnap_2021_Temperature_workings$Temperature_n_with_Temperature_low) + 
  as.numeric(nnap_2021_Temperature_workings$Temperature_n_with_Temperature_high)

nnap_2021_Temperature <-
  data.frame(
    Unit_name=
      nnap_2021_Temperature_workings$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2021_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2021_Temperature_workings$Temperature_n_with_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2021_Temperature_workings$Temperature_n_with_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2021_Temperature_workings$Temperature_n_with_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2021_Temperature_workings$Temperature_n_with_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2021_Temperature_workings$Temperature_n_missing_Temperature_data)
  )
```

```{r, 2022 Temperature}
nnap_2022_Temperature_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_Temp$Unit_name,
    
    Temperature_n_eligible=
      as.numeric(nnap_2022_data_0_Temp$NumberOfEligibleBabies_Temp),

    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2022_data_0_Temp$Outcome_Temp),
    
    Temperature_n_with_Temperature_low=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Temp$TempLT32_Temp)
        ) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$Temp32359_Temp)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$Temp36364_Temp)))) ,
    
    Temperature_n_with_Temperature_high=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$TempGT375_Temp)))) ,
    Temperature_n_with_normothermia_yes=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$Temp365375_Temp)))),
    Temperature_n_missing_Temperature_data=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$MissingUnknownData_Temp)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$AfterAnHour_Temp)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2022_data_0_Temp$NotTakenAfterAdmission_Temp))))
)

nnap_2022_Temperature_workings$Temperature_n_with_normothermia_no <-
  as.numeric(nnap_2022_Temperature_workings$Temperature_n_with_Temperature_low) + 
  as.numeric(nnap_2022_Temperature_workings$Temperature_n_with_Temperature_high)

nnap_2022_Temperature <-
  data.frame(
    Unit_name=
      nnap_2022_Temperature_workings$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2022_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2022_Temperature_workings$Temperature_n_with_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2022_Temperature_workings$Temperature_n_with_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2022_Temperature_workings$Temperature_n_with_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2022_Temperature_workings$Temperature_n_with_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2022_Temperature_workings$Temperature_n_missing_Temperature_data)
  )
```

```{r, 2023 Temperature}
nnap_2023_Temperature_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_Norm_Temp$Unit_name,
    
    Temperature_n_eligible=
      as.numeric(nnap_2023_data_masked_Norm_Temp$Count_Norm_Temp),

    Temperature_n_with_Temperature_data=
      as.numeric(nnap_2023_data_masked_Norm_Temp$Outcome_Norm_Temp),
    
    Temperature_n_with_Temperature_low=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Norm_Temp$`On_Time_-_Less_32_Norm_Temp`)
        ) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$`On_Time_-_32-_36_Norm_Temp`)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$`On_Time-_36_-_36half_Norm_Temp`)))) ,
    
    Temperature_n_with_Temperature_high=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$`On_Time_-_More-_37_half_Norm_Temp`)))) ,
    Temperature_n_with_normothermia_yes=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$`On_Time_-_36_half_-37_half_Norm_Temp`)))),
    Temperature_n_missing_Temperature_data=
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$Missing_Norm_Temp)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$After_hour_Norm_Temp)))) +
        as.numeric(
          (gsub("[^0-9]", "", 
                gsub("\\(.*\\)", "",
                     nnap_2023_data_masked_Norm_Temp$Not_taken_Norm_Temp))))
)

nnap_2023_Temperature_workings$Temperature_n_with_normothermia_no <-
  as.numeric(nnap_2023_Temperature_workings$Temperature_n_with_Temperature_low) + 
  as.numeric(nnap_2023_Temperature_workings$Temperature_n_with_Temperature_high)

nnap_2023_Temperature <-
  data.frame(
    Unit_name=
      nnap_2023_Temperature_workings$Unit_name,
    Temperature_n_eligible=
      as.numeric(nnap_2023_Temperature_workings$Temperature_n_eligible),
    Temperature_n_normothermia_yes=
      as.numeric(nnap_2023_Temperature_workings$Temperature_n_with_normothermia_yes),
    Temperature_n_normothermia_no=
      as.numeric(nnap_2023_Temperature_workings$Temperature_n_with_normothermia_no),
    Temperature_n_Temperature_low=
      as.numeric(nnap_2023_Temperature_workings$Temperature_n_with_Temperature_low),
    Temperature_n_Temperature_high=
      as.numeric(nnap_2023_Temperature_workings$Temperature_n_with_Temperature_high),
    Temperature_n_missing_Temperature_data=
      as.numeric(nnap_2023_Temperature_workings$Temperature_n_missing_Temperature_data)
  )
```


******************************************************************************************************************************************
antenatal steroids
*********************************************************************************************************************************************

```{r, 2017 ANS}
nnap_2017_ANS_workings <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Antenatal_steroids$Unit_name,
    ANS_n_eligible=
      as.numeric(nnap_2017_data_0_Antenatal_steroids$Eligible_mothers_Antenatal_steroids),
    ANS_n_with_ANS_data=
      as.numeric(nnap_2017_data_0_Antenatal_steroids$With_outcome_Antenatal_steroids),

    ANS_n_ANS_yes=
      as.numeric(nnap_2017_data_0_Antenatal_steroids$Steroids_given_number_Antenatal_steroids),
    ANS_n_ANS_no=
      as.numeric(nnap_2017_data_0_Antenatal_steroids$Steroids_not_given_number_Antenatal_steroids)
)

nnap_2017_ANS <-
  data.frame(
    Unit_name=
      nnap_2017_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2017_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2017_ANS_workings$ANS_n_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2017_ANS_workings$ANS_n_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2017_ANS_workings$ANS_n_ANS_missing)
 )
```

```{r, 2018 ANS}
nnap_2018_ANS_workings <-
  data.frame(
    Unit_name=
      gsub("\\d", "", x=nnap_2018_data_Antenatal_steroids$Unit_name),
    ANS_n_eligible=
      as.numeric(nnap_2018_data_Antenatal_steroids$Count_eligible_mothers_Antenatal_steroids),

    ANS_n_with_ANS_data=
      as.numeric(nnap_2018_data_Antenatal_steroids$With_outcome_Antenatal_steroids),
    
    ANS_n_without_ANS_no=
      as.numeric(
        sub(" .*", "", nnap_2018_data_Antenatal_steroids$Steroids_not_given_Antenatal_steroids)
        ),
    
    ANS_n_with_ANS_yes=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Antenatal_steroids$Steroids_given_Antenatal_steroids)
        ),
    ANS_n_missing_ANS_data=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Antenatal_steroids$Missing_data_Antenatal_steroids)
        )
)
nnap_2018_ANS <-
  data.frame(
    Unit_name=
      nnap_2018_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2018_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2018_ANS_workings$ANS_n_with_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2018_ANS_workings$ANS_n_without_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2018_ANS_workings$ANS_n_missing_ANS_data)
  )

```

```{r, 2019 ANS}
nnap_2019_ANS_workings <-
  data.frame(
    Unit_name=
      nnap_2019_data_Antenatal_steroids$Unit_name,
    ANS_n_eligible=
      as.numeric(nnap_2019_data_Antenatal_steroids$Eligible_mothers_Antenatal_steroids),

    ANS_n_with_ANS_data=
      as.numeric(nnap_2019_data_Antenatal_steroids$Outcome_Antenatal_steroids),
    
    ANS_n_without_ANS_no=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Antenatal_steroids$`Steroids_not_given_(%)_Antenatal_steroids`)
        ),
    
    ANS_n_with_ANS_yes=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Antenatal_steroids$`Steroids_given_(as_%_of_all_eligible_mothers)_Antenatal_steroids`)
        ),
    ANS_n_missing_ANS_data=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Antenatal_steroids$`Missing/Unknown_data_(%)_Antenatal_steroids`)
        )
)

nnap_2019_ANS <-
  data.frame(
    Unit_name=
      nnap_2019_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2019_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2019_ANS_workings$ANS_n_with_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2019_ANS_workings$ANS_n_without_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2019_ANS_workings$ANS_n_missing_ANS_data)
  )
```

```{r, 2020 ANS}
nnap_2020_ANS_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_Antenatal_steroids$Unit_name,
    ANS_n_eligible=
      as.numeric(nnap_2020_data_Antenatal_steroids$Eligible_mothers_Antenatal_steroids),

    ANS_n_with_ANS_data=
      as.numeric(nnap_2020_data_Antenatal_steroids$Outcome_Antenatal_steroids),
    
    ANS_n_without_ANS_no=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Antenatal_steroids$`Steroids_not_given_(%)_Antenatal_steroids`)
        ),
    
    ANS_n_with_ANS_yes=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Antenatal_steroids$`Steroids_given_(as_a_%_of_all_mothers_with_Outcome)_Antenatal_steroids`)
        ),
    ANS_n_missing_ANS_data=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Antenatal_steroids$`Missing/Unknown_data_(%)_Antenatal_steroids`)
        )
)

nnap_2020_ANS_workings$check_missing <- 
  as.numeric(nnap_2020_ANS_workings$ANS_n_eligible) - 
  as.numeric(nnap_2020_ANS_workings$ANS_n_without_ANS_no) - 
  as.numeric(nnap_2020_ANS_workings$ANS_n_with_ANS_yes) -
  as.numeric(nnap_2020_ANS_workings$ANS_n_missing_ANS_data) 

nnap_2020_ANS <-
  data.frame(
    Unit_name=
      nnap_2020_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2020_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2020_ANS_workings$ANS_n_with_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2020_ANS_workings$ANS_n_without_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2020_ANS_workings$ANS_n_missing_ANS_data)
  )
```

```{r, 2021 ANS}
nnap_2021_ANS_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_Antenatal_steroids$Unit_name,
    
    ANS_n_eligible=
      as.numeric(nnap_2021_data_Antenatal_steroids$Eligible_mothers_Antenatal_steroids),

    ANS_n_with_ANS_data=
      as.numeric(nnap_2021_data_Antenatal_steroids$Outcome_Antenatal_steroids),
    
    ANS_n_with_ANS_yes=
        as.numeric(
          sub(" .*", "",
              nnap_2021_data_Antenatal_steroids$`Steroids_given_(as_a_%_of_all_mothers_with_Outcome)_Antenatal_steroids`)),
    ANS_n_without_ANS_no=
        as.numeric(
          sub(" .*", "",
              nnap_2021_data_Antenatal_steroids$`Steroids_not_given_(%)_Antenatal_steroids`)),
    ANS_n_missing_ANS_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_Antenatal_steroids$`Missing/Unknown_data_(%)_Antenatal_steroids`)
        )
)

nnap_2021_ANS <-
  data.frame(
    Unit_name=
      nnap_2021_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2021_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2021_ANS_workings$ANS_n_with_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2021_ANS_workings$ANS_n_without_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2021_ANS_workings$ANS_n_missing_ANS_data)
  )
```

```{r, 2022 ANS}
nnap_2022_ANS_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_Steroids$Unit_name,
    
    ANS_n_eligible=
      as.numeric(nnap_2022_data_0_Steroids$NumberOfEligibleMothers_Steroids),

    ANS_n_with_ANS_data=
      as.numeric(nnap_2022_data_0_Steroids$Outcome_Steroids),
    
    ANS_n_with_ANS_yes=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Steroids$Given_Steroids)
        ),
    ANS_n_without_ANS_no=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Steroids$NotGiven_Steroids)
        ),
    ANS_n_missing_ANS_data=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Steroids$Missing_Steroids)
        )
)

nnap_2022_ANS_workings <-
  nnap_2022_ANS_workings %>%
  filter(Unit_name!="ALLPARTICIPATINGUNITS") %>%
  filter(!is.na(Unit_name))

nnap_2022_ANS <-
  data.frame(
    Unit_name=
      nnap_2022_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2022_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2022_ANS_workings$ANS_n_with_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2022_ANS_workings$ANS_n_without_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2022_ANS_workings$ANS_n_missing_ANS_data)
  )
```

```{r, 2023 ANS}
nnap_2023_ANS_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_Steroids$Unit_name,
    ANS_n_eligible=
      as.numeric(nnap_2023_data_masked_Steroids$Eligible_Steroids),

    ANS_n_with_ANS_data=
      as.numeric(nnap_2023_data_masked_Steroids$With_outcome_Steroids),
    
    ANS_n_with_ANS_yes=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Steroids$Proportion_Steroids)
        ),
    ANS_n_without_ANS_no=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Steroids$Steroids_not_given_Steroids)
        ),
    
    ANS_n_missing_ANS_data=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Steroids$Missing_Steroids)
        )
)

nnap_2023_ANS <-
  data.frame(
    Unit_name=
      nnap_2023_ANS_workings$Unit_name,
    ANS_n_alive_and_dead_eligible=
      as.numeric(nnap_2023_ANS_workings$ANS_n_eligible),
    ANS_n_yes_ANS=
      as.numeric(nnap_2023_ANS_workings$ANS_n_with_ANS_yes),
    ANS_n_no_ANS=
      as.numeric(nnap_2023_ANS_workings$ANS_n_without_ANS_no),
    ANS_n_missing_ANS_data=
      as.numeric(nnap_2023_ANS_workings$ANS_n_missing_ANS_data)
  )
```

***********************************************
Magnesium sulphate antenatal administration
***********************************************

```{r, 2017 MgSO}
nnap_2017_MgSO_workings <-
  data.frame(
    
    Unit_name=
      nnap_2017_data_0_Antenatal_magnesium_sulphate$Unit_name,
    MgSO_n_eligible=
      as.numeric(nnap_2017_data_0_Antenatal_magnesium_sulphate$Eligible_mothers_Antenatal_magnesium_sulphate),
    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2017_data_0_Antenatal_magnesium_sulphate$With_outcome_Antenatal_magnesium_sulphate),

    MgSO_n_MgSO_yes=
      as.numeric(nnap_2017_data_0_Antenatal_magnesium_sulphate$Magnesium_sulphate_given_number_Antenatal_magnesium_sulphate),
    MgSO_n_MgSO_no=
      as.numeric(nnap_2017_data_0_Antenatal_magnesium_sulphate$Magnesium_sulphate_not_given_number_Antenatal_magnesium_sulphate)
)

nnap_2017_MgSO_workings$MgSO_n_MgSO_missing <-
  nnap_2017_MgSO_workings$MgSO_n_eligible -
  nnap_2017_MgSO_workings$MgSO_n_with_MgSO_data

nnap_2017_MgSO <-
  data.frame(
    Unit_name=
      nnap_2017_MgSO_workings$Unit_name,
    MgSO_n_alive_and_dead_eligible=
      as.numeric(nnap_2017_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2017_MgSO_workings$MgSO_n_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2017_MgSO_workings$MgSO_n_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2017_MgSO_workings$MgSO_n_MgSO_missing)
 )
```

```{r, 2018 MgSO}
nnap_2018_MgSO_workings <-
  data.frame(
    Unit_name=
      gsub("\\d", "", x=nnap_2018_data_Antenatal_magnesium_sulphate$Unit_name),
    MgSO_n_eligible=
      as.numeric(nnap_2018_data_Antenatal_magnesium_sulphate$Count_eligible_mothers_Antenatal_magnesium_sulphate),

    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2018_data_Antenatal_magnesium_sulphate$With_outcome_Antenatal_magnesium_sulphate),
    
    MgSO_n_without_MgSO_no=
      as.numeric(nnap_2018_data_Antenatal_magnesium_sulphate$Magnesium_not_given_Antenatal_magnesium_sulphate),
    
    MgSO_n_with_MgSO_yes=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Antenatal_magnesium_sulphate$Magnesium_given_Antenatal_magnesium_sulphate)
        ),
    MgSO_n_missing_MgSO_data=
        as.numeric(
          sub(" .*", "", nnap_2018_data_Antenatal_magnesium_sulphate$Missing_data_Antenatal_magnesium_sulphate)
        )
)

nnap_2018_MgSO <-
  data.frame(
    Unit_name=
      nnap_2018_MgSO_workings$Unit_name,
    MgSO_n_eligible=
      as.numeric(nnap_2018_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2018_MgSO_workings$MgSO_n_with_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2018_MgSO_workings$MgSO_n_without_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2018_MgSO_workings$MgSO_n_missing_MgSO_data)
  )

```

```{r, 2019 MgSO}
nnap_2019_MgSO_workings <-
  data.frame(
    Unit_name=
      nnap_2019_data_Antenatal_magnesium_sulphate$Unit_name,
    MgSO_n_eligible=
      as.numeric(nnap_2019_data_Antenatal_magnesium_sulphate$Eligible_mothers_Antenatal_magnesium_sulphate),

    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2019_data_Antenatal_magnesium_sulphate$Number_of_eligible_mothers_with_outcome_Antenatal_magnesium_sulphate),
    
    MgSO_n_without_MgSO_no=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Antenatal_magnesium_sulphate$`Not_given_(%)_Antenatal_magnesium_sulphate`)
        ),
    
    MgSO_n_with_MgSO_yes=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Antenatal_magnesium_sulphate$`Given_(%)_Antenatal_magnesium_sulphate`)
        ),
    MgSO_n_missing_MgSO_data=
        as.numeric(
          sub(" .*", "", nnap_2019_data_Antenatal_magnesium_sulphate$`Missing_data_(%)_Antenatal_magnesium_sulphate`)
        )
)

nnap_2019_MgSO <-
  data.frame(
    Unit_name=
      nnap_2019_MgSO_workings$Unit_name,
    MgSO_n_alive_and_dead_eligible=
      as.numeric(nnap_2019_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2019_MgSO_workings$MgSO_n_with_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2019_MgSO_workings$MgSO_n_without_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2019_MgSO_workings$MgSO_n_missing_MgSO_data)
  )

```

```{r, 2020 MgSO}
nnap_2020_MgSO_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_Magnesium_sulphate$Unit_name,
    MgSO_n_eligible=
      as.numeric(nnap_2020_data_Magnesium_sulphate$Eligible_mothers_Magnesium_sulphate),

    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2020_data_Magnesium_sulphate$Number_of_eligible_mothers_with_outcome_Magnesium_sulphate),
    
    MgSO_n_without_MgSO_no=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Magnesium_sulphate$`Not_given_(%)_Magnesium_sulphate`)
        ),
    
    MgSO_n_with_MgSO_yes=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Magnesium_sulphate$`Given_(%)_Magnesium_sulphate`)
        ),
    MgSO_n_missing_MgSO_data=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Magnesium_sulphate$`Missing_data_(%)_Magnesium_sulphate`)
        )
)

nnap_2020_MgSO <-
  data.frame(
    Unit_name=
      nnap_2020_MgSO_workings$Unit_name,
    MgSO_n_alive_and_dead_eligible=
      as.numeric(nnap_2020_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2020_MgSO_workings$MgSO_n_with_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2020_MgSO_workings$MgSO_n_without_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2020_MgSO_workings$MgSO_n_missing_MgSO_data)
  )
```

```{r, 2021 MgSO}
nnap_2021_MgSO_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_Antenatal_magnesium_sulphate$Unit_name,
    
    MgSO_n_eligible=
      as.numeric(nnap_2021_data_Antenatal_magnesium_sulphate$Eligible_mothers_Antenatal_magnesium_sulphate),

    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2021_data_Antenatal_magnesium_sulphate$Number_of_eligible_mothers_with_outcome_Antenatal_magnesium_sulphate),
    
    MgSO_n_with_MgSO_yes=
        as.numeric(
          sub(" .*", "",
              nnap_2021_data_Antenatal_magnesium_sulphate$`Given_(%)_Antenatal_magnesium_sulphate`)),
    MgSO_n_without_MgSO_no=
        as.numeric(
          sub(" .*", "",
              nnap_2021_data_Antenatal_magnesium_sulphate$`Not_given_(%)_Antenatal_magnesium_sulphate`)),
    MgSO_n_missing_MgSO_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_Antenatal_magnesium_sulphate$`Missing_data_(%)_Antenatal_magnesium_sulphate`)
        )
)


nnap_2021_MgSO <-
  data.frame(
    Unit_name=
      nnap_2021_MgSO_workings$Unit_name,
    MgSO_n_eligible=
      as.numeric(nnap_2021_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2021_MgSO_workings$MgSO_n_with_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2021_MgSO_workings$MgSO_n_without_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2021_MgSO_workings$MgSO_n_missing_MgSO_data)
  )
```

```{r, 2022 MgSO}
nnap_2022_MgSO_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_Mag_Sulph$Unit_name,
    
    MgSO_n_eligible=
      as.numeric(nnap_2022_data_0_Mag_Sulph$MAGBabiesCount_Mag_Sulph),

    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2022_data_0_Mag_Sulph$Outcome_Mag_Sulph),
    
    MgSO_n_with_MgSO_yes=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Mag_Sulph$MAGGiven_Mag_Sulph)
        ),
    MgSO_n_without_MgSO_no=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Mag_Sulph$MAGNotGiven_Mag_Sulph)
        ),
    MgSO_n_missing_MgSO_data=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_Mag_Sulph$MAGMissing_Mag_Sulph)
        )
)

nnap_2022_MgSO_workings <-
  nnap_2022_MgSO_workings %>%
  filter(Unit_name!="ALLPARTICIPATINGUNITS") %>%
  filter(!is.na(Unit_name))

nnap_2022_MgSO <-
  data.frame(
    Unit_name=
      nnap_2022_MgSO_workings$Unit_name,
    MgSO_n_alive_and_dead_eligible=
      as.numeric(nnap_2022_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2022_MgSO_workings$MgSO_n_with_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2022_MgSO_workings$MgSO_n_without_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2022_MgSO_workings$MgSO_n_missing_MgSO_data)
  )

```

```{r, 2023 MgSO}
nnap_2023_MgSO_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_Mag_Sulphate$Unit_name,
    MgSO_n_eligible=
      as.numeric(nnap_2023_data_masked_Mag_Sulphate$Eligible_Mag_Sulphate),

    MgSO_n_with_MgSO_data=
      as.numeric(nnap_2023_data_masked_Mag_Sulphate$With_outcome_Mag_Sulphate),
    
    MgSO_n_with_MgSO_yes=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Mag_Sulphate$MagYes_Mag_Sulphate)
        ),

    MgSO_n_without_MgSO_no=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Mag_Sulphate$MagNo_Mag_Sulphate)
        ),

    MgSO_n_missing_MgSO_data=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_Mag_Sulphate$Missing_Mag_Sulphate)
        )
)

nnap_2023_MgSO <-
  data.frame(
    Unit_name=
      nnap_2023_MgSO_workings$Unit_name,
    MgSO_n_alive_and_dead_eligible=
      as.numeric(nnap_2023_MgSO_workings$MgSO_n_eligible),
    MgSO_n_yes_MgSO=
      as.numeric(nnap_2023_MgSO_workings$MgSO_n_with_MgSO_yes),
    MgSO_n_no_MgSO=
      as.numeric(nnap_2023_MgSO_workings$MgSO_n_without_MgSO_no),
    MgSO_n_missing_MgSO_data=
      as.numeric(nnap_2023_MgSO_workings$MgSO_n_missing_MgSO_data)
  )
```

*******************************************************************************************************************************************
antenatal delayed cord clamping
******************************************************************************************************************

started reporting 2019

```{r, 2017 to 2019 DCC are all created as NA}
nnap_2017_DCC <-
  data.frame(
    Unit_name=nnap_2017_data_0_Bronchopulmonary_dysplasia$Unit_name,
    DCC_n_eligible=as.numeric(NA),
    DCC_n_yes_DCC=as.numeric(NA),
    DCC_n_no_DCC=as.numeric(NA),
    DCC_n_missing_DCC_data=as.numeric(NA)
  )

nnap_2018_DCC <-
  data.frame(
    Unit_name=gsub("\\d", "", x=nnap_2018_data_Bronchopulmonary_dysplasia$Unit_name),
    DCC_n_eligible=as.numeric(NA),
    DCC_n_yes_DCC=as.numeric(NA),
    DCC_n_no_DCC=as.numeric(NA),
    DCC_n_missing_DCC_data=as.numeric(NA)
  )

nnap_2019_DCC <-
  data.frame(
    Unit_name=nnap_2019_data_BPD$Unit_name,
    DCC_n_eligible=as.numeric(NA),
    DCC_n_yes_DCC=as.numeric(NA),
    DCC_n_no_DCC=as.numeric(NA),
    DCC_n_missing_DCC_data=as.numeric(NA)
  )

```

```{r, 2020 DCC}
nnap_2020_DCC_workings <-
  data.frame(
    Unit_name=
      nnap_2020_data_Deferred_cord_clamping$Unit_name,
    DCC_n_eligible=
      as.numeric(nnap_2020_data_Deferred_cord_clamping$Number_Of_Eligible_Babies_Deferred_cord_clamping),

    DCC_n_with_DCC_data=
      as.numeric(nnap_2020_data_Deferred_cord_clamping$Outcome_Deferred_cord_clamping),
    
    DCC_n_without_DCC_no=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Deferred_cord_clamping$Immediate_Deferred_cord_clamping)
        ),
    
    DCC_n_with_DCC_yes=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Deferred_cord_clamping$Deferred_Deferred_cord_clamping)
        ),
    DCC_n_missing_DCC_data=
        as.numeric(
          sub(" .*", "", nnap_2020_data_Deferred_cord_clamping$Missing_Data_Deferred_cord_clamping)
        )
)

nnap_2020_DCC <-
  data.frame(
    Unit_name=
      nnap_2020_DCC_workings$Unit_name,
    DCC_n_eligible=
      as.numeric(nnap_2020_DCC_workings$DCC_n_eligible),
    DCC_n_yes_DCC=
      as.numeric(nnap_2020_DCC_workings$DCC_n_with_DCC_yes),
    DCC_n_no_DCC=
      as.numeric(nnap_2020_DCC_workings$DCC_n_without_DCC_no),
    DCC_n_missing_DCC_data=
      as.numeric(nnap_2020_DCC_workings$DCC_n_missing_DCC_data)
  )
```

```{r, 2021 DCC}
nnap_2021_DCC_workings <-
  data.frame(
    Unit_name=
      nnap_2021_data_Deferred_cord_clamping$Unit_name,
    
    DCC_n_eligible=
      as.numeric(nnap_2021_data_Deferred_cord_clamping$Number_Of_Eligible_Babies_Deferred_cord_clamping),

    DCC_n_with_DCC_data=
      as.numeric(nnap_2021_data_Deferred_cord_clamping$Outcome_Deferred_cord_clamping),
    
    DCC_n_with_DCC_yes=
        as.numeric(
          sub(" .*", "",
              nnap_2021_data_Deferred_cord_clamping$Deferred_Deferred_cord_clamping)),
    DCC_n_without_DCC_no=
        as.numeric(
          sub(" .*", "",
              nnap_2021_data_Deferred_cord_clamping$Immediate_Deferred_cord_clamping)),
    DCC_n_missing_DCC_data=
        as.numeric(
          sub(" .*", "", nnap_2021_data_Deferred_cord_clamping$Missing_Data_Deferred_cord_clamping)
        )
)

nnap_2021_DCC <-
  data.frame(
    Unit_name=
      nnap_2021_DCC_workings$Unit_name,
    DCC_n_eligible=
      as.numeric(nnap_2021_DCC_workings$DCC_n_eligible),
    DCC_n_yes_DCC=
      as.numeric(nnap_2021_DCC_workings$DCC_n_with_DCC_yes),
    DCC_n_no_DCC=
      as.numeric(nnap_2021_DCC_workings$DCC_n_without_DCC_no),
    DCC_n_missing_DCC_data=
      as.numeric(nnap_2021_DCC_workings$DCC_n_missing_DCC_data)
  )
```

```{r, 2022 DCC}
nnap_2022_DCC_workings <-
  data.frame(
    Unit_name=
      nnap_2022_data_0_DCC$Unit_name,
    
    DCC_n_eligible=
      as.numeric(nnap_2022_data_0_DCC$DCCEligibleBabies_DCC),

    DCC_n_with_DCC_data=
      as.numeric(nnap_2022_data_0_DCC$DCCOutcome_DCC),
    
    DCC_n_with_DCC_yes=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_DCC$DCCDeferred_DCC)
        ),
    DCC_n_without_DCC_no=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_DCC$DCCImmediate_DCC)
        ),
    DCC_n_missing_DCC_data=
        as.numeric(
          sub(" .*", "", nnap_2022_data_0_DCC$DCCMissing_DCC)
        )
)

#manually remove the totals column from this sheet
nnap_2022_DCC_workings <-
  nnap_2022_DCC_workings %>%
  filter(Unit_name!="ALLPARTICIPATINGUNITS") %>%
  filter(!is.na(Unit_name))

nnap_2022_DCC <-
  data.frame(
    Unit_name=
      nnap_2022_DCC_workings$Unit_name,
    DCC_n_eligible=
      as.numeric(nnap_2022_DCC_workings$DCC_n_eligible),
    DCC_n_yes_DCC=
      as.numeric(nnap_2022_DCC_workings$DCC_n_with_DCC_yes),
    DCC_n_no_DCC=
      as.numeric(nnap_2022_DCC_workings$DCC_n_without_DCC_no),
    DCC_n_missing_DCC_data=
      as.numeric(nnap_2022_DCC_workings$DCC_n_missing_DCC_data)
  )
```

```{r, 2023 DCC}
nnap_2023_DCC_workings <-
  data.frame(
    Unit_name=
      nnap_2023_data_masked_DCC$Unit_name,
    DCC_n_eligible=
      as.numeric(nnap_2023_data_masked_DCC$Eligible_DCC),

    DCC_n_with_DCC_data=
      as.numeric(nnap_2023_data_masked_DCC$With_outcome_DCC),
    
    DCC_n_with_DCC_one_to_two_minutes=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_DCC$Up_To_2_Minutes_DCC)
        ),

    DCC_n_with_DCC_over_two_minutes=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_DCC$More_Than_2_Minutes_DCC)
        ),

    DCC_n_without_DCC_no=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_DCC$Less_Than_1_Minute_DCC)
        ),

    DCC_n_missing_DCC_data=
        as.numeric(
          sub(" .*", "", nnap_2023_data_masked_DCC$Missing_DCC)
        )
)

nnap_2023_DCC_workings$DCC_n_with_DCC_yes <-
  nnap_2023_DCC_workings$DCC_n_with_DCC_one_to_two_minutes +
  nnap_2023_DCC_workings$DCC_n_with_DCC_over_two_minutes

nnap_2023_DCC <-
  data.frame(
    Unit_name=
      nnap_2023_DCC_workings$Unit_name,
    DCC_n_eligible=
      as.numeric(nnap_2023_DCC_workings$DCC_n_eligible),
    DCC_n_yes_DCC=
      as.numeric(nnap_2023_DCC_workings$DCC_n_with_DCC_yes),
    DCC_n_no_DCC=
      as.numeric(nnap_2023_DCC_workings$DCC_n_without_DCC_no),
    DCC_n_missing_DCC_data=
      as.numeric(nnap_2023_DCC_workings$DCC_n_missing_DCC_data)
  )
```



*******************************************************************************************************************************************
joining frames and adding organisation names
*********************************************************************************************************************************************

```{r, helper function to combine all metrics into one frame for one year}
combine_nnap_data_for_same_year <- function(year) {
  
  level <- get(paste0("nnap_", year, "_unit_level"))
  bpd   <- get(paste0("nnap_", year, "_bpd"))
  NEC   <- get(paste0("nnap_", year, "_NEC"))
  sepsis<- get(paste0("nnap_", year, "_sepsis"))
  IVH   <- get(paste0("nnap_", year, "_IVH"))
  cPVL  <- get(paste0("nnap_", year, "_cPVL"))
  DCC   <- get(paste0("nnap_", year, "_DCC"))
  ANS   <- get(paste0("nnap_", year, "_ANS"))
  MgSO   <- get(paste0("nnap_", year, "_MgSO"))
  temp   <- get(paste0("nnap_", year, "_Temperature"))
  
  all_nnap_data_for_year <-
    level %>%
    full_join(bpd,   by = join_by(Unit_name)) %>%
    full_join(NEC,   by = join_by(Unit_name)) %>%
    full_join(sepsis, by = join_by(Unit_name)) %>%
    full_join(IVH, by = join_by(Unit_name)) %>%
    full_join(cPVL, by = join_by(Unit_name)) %>%
    full_join(DCC, by = join_by(Unit_name)) %>%
    full_join(ANS, by = join_by(Unit_name)) %>%
    full_join(MgSO, by = join_by(Unit_name)) %>%
    full_join(temp, by = join_by(Unit_name))
  
  manual_unit_levels <- 
    read.csv("manual_unit_level_definition/NNAP_manual_unit_levels_to_add.csv")

  all_nnap_data_for_year_with_manual_unit_level <- 
    left_join(all_nnap_data_for_year, manual_unit_levels, by = "Unit_name")
  
  all_nnap_data_for_year_with_manual_unit_level <- 
    all_nnap_data_for_year_with_manual_unit_level %>%
    mutate(Unit_level = ifelse(is.na(Unit_level), Unit_level_manual, Unit_level))
}

for (yr in 2017:2023) {
  merged <- combine_nnap_data_for_same_year(yr)
  assign(paste0("nnap_", yr), merged)
}
```

***************************************
load MBRRACE data
**********************************************************************************

```{r, load all the MBRRACE data frames of total mortality data and modernise the trust names}
library(stringr)

folder_path <- "MBRRACE_raw_data/total_mortality"

if (!dir.exists(folder_path)) {
  stop(paste("Error: The folder '", folder_path, "' does not exist. Please check the path."))
}

csv_files <- list.files(
  path = folder_path,
  pattern = "\\.csv$",
  full.names = TRUE,
  ignore.case = TRUE
)

if (length(csv_files) == 0) {
  message(paste("No CSV files found in:", folder_path))
} else {
  message(paste(length(csv_files), "CSV files found. Starting conversion..."))
}

for (file_path in csv_files) {

  file_name_full <- basename(file_path)

  file_name_base <- sub("\\.csv$", "", file_name_full, ignore.case = TRUE)

  clean_file_name <- str_replace_all(file_name_base, "[^[:alnum:]_]", "_")
  clean_file_name <- str_replace_all(clean_file_name, "_+", "_")
  clean_file_name <- str_replace_all(clean_file_name, "^_+|_+$", "")
  year_match <- str_extract(clean_file_name, "\\d{4}")
  year_to_add <- ifelse(is.na(year_match), "UnknownYear", year_match)
  df_name <- clean_file_name

  message(paste("Processing file:", file_name_full, "-> Target DF:", df_name))
  tryCatch({
    data_frame <- read.csv(
      file = file_path,
      header = TRUE, 
      stringsAsFactors = FALSE 
    )

          if ("OrganisationName" %in% names(data_frame)) { 
      data_frame$OrganisationName_original <- data_frame$OrganisationName 
      data_frame$OrganisationName <- 
        toupper(
          gsub("[[:space:][:punct:]]", "", data_frame$OrganisationName))
          }
    
        data_frame$OrganisationName <- gsub("&", "AND", data_frame$OrganisationName)
        data_frame$OrganisationName <- gsub("[()]", "", data_frame$OrganisationName)
    
    data_frame <- data_frame %>%
        rename(Trust_name = OrganisationName)
    
    data_frame$Trust_name_original <- data_frame$Trust_name
    
      data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="YEOVILDISTRICTHOSPITALNHSFOUNDATIONTRUST",
        "SOMERSETNHSFOUNDATIONTRUST",
        data_frame$Trust_name) 

      data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="HOMERTONUNIVERSITYHOSPITALNHSFOUNDATIONTRUST",
        "HOMERTONHEALTHCARENHSFOUNDATIONTRUST",
        data_frame$Trust_name)  
      
            data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="BEDFORDHOSPITALNHSTRUST",
        "BEDFORDSHIREHOSPITALSNHSFOUNDATIONTRUST",
        data_frame$Trust_name)  
            data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="LUTONANDDUNSTABLEUNIVERSITYHOSPITALNHSFOUNDATIONTRUST",
        "BEDFORDSHIREHOSPITALSNHSFOUNDATIONTRUST",
        data_frame$Trust_name)  
            
                        data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="THEPENNINEACUTEHOSPITALSNHSTRUST",
        "NORTHERNCAREALLIANCENHSFOUNDATIONTRUST",
        data_frame$Trust_name) 
                        
                        data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="TAUNTONANDSOMERSETNHSFOUNDATIONTRUST",
        "SOMERSETNHSFOUNDATIONTRUST",
        data_frame$Trust_name) 
            
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="COLCHESTERHOSPITALUNIVERSITYNHSFOUNDATIONTRUST",
        "EASTSUFFOLKANDNORTHESSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="THEIPSWICHHOSPITALNHSTRUST",
        "EASTSUFFOLKANDNORTHESSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="BURTONHOSPITALSNHSFOUNDATIONTRUST",
        "UNIVERSITYHOSPITALSOFDERBYANDBURTONNHSFOUNDATIONTRUST",
        data_frame$Trust_name)

        data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="LEWISHAMANDGREENWICHNHSTRUST",
        "LEWISHAMANDGREENWICHNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="MIDESSEXHOSPITALSERVICESNHSTRUST",
        "MIDANDSOUTHESSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SOUTHENDUNIVERSITYHOSPITALNHSFOUNDATIONTRUST",
        "MIDANDSOUTHESSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
        data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="OXFORDUNIVERSITYHOSPITALSNHSFOUNDATIONTRUST",
        "OXFORDUNIVERSITYHOSPITALSNHSTRUST",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="PLYMOUTHHOSPITALSNHSTRUST",
        "UNIVERSITYHOSPITALSPLYMOUTHNHSTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SOUTHDEVONHEALTHCARENHSFOUNDATIONTRUST",
        "TORBAYANDSOUTHDEVONNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="NORTHERNDEVONHEALTHCARENHSTRUST",
        "ROYALDEVONUNIVERSITYHEALTHCARENHSFOUNDATIONTRUST",
        data_frame$Trust_name)

    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="ROYALDEVONANDEXETERNHSFOUNDATIONTRUST",
        "ROYALDEVONUNIVERSITYHEALTHCARENHSFOUNDATIONTRUST",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="WESTERNSUSSEXHOSPITALSNHSFOUNDATIONTRUST",
        "UNIVERSITYHOSPITALSSUSSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="BRIGHTONANDSUSSEXUNIVERSITYHOSPITALSNHSTRUST",
        "UNIVERSITYHOSPITALSSUSSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="WARRINGTONANDHALTONHOSPITALSNHSFOUNDATIONTRUST",
        "WARRINGTONANDHALTONTEACHINGHOSPITALSNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="HEARTOFENGLANDNHSFOUNDATIONTRUST",
        "BIRMINGHAMWOMENSANDCHILDRENSNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="HULLANDEASTYORKSHIREHOSPITALSNHSTRUST",
        "HULLUNIVERSITYTEACHINGHOSPITALSNHSTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="ISLEOFMANDEPARTMENTOFHEALTHANDSOCIALCARE",
        "MANXCARE",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="TAMESIDEHOSPITALNHSFOUNDATIONTRUST",
        "TAMESIDEANDGLOSSOPINTEGRATEDCARENHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="THEDUDLEYGROUPNHSFOUNDATIONTRUST",
        "SANDWELLANDWESTBIRMINGHAMHOSPITALSNHSTRUST",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="STHELENSANDKNOWSLEYTEACHINGHOSPITALSNHSTRUST",
        "MERSEYANDWESTLANCASHIRETEACHINGHOSPITALSNHSTRUST",
        data_frame$Trust_name)
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SOUTHPORTANDORMSKIRKHOSPITALNHSTRUST",
        "MERSEYANDWESTLANCASHIRETEACHINGHOSPITALSNHSTRUST",
        data_frame$Trust_name)
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SOUTHPORTORMSKIRKHOSPITALNHSTRUST",
        "MERSEYANDWESTLANCASHIRETEACHINGHOSPITALSNHSTRUST",
        data_frame$Trust_name)
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SOUTHWARWICKSHIRENHSFOUNDATIONTRUST",
        "SOUTHWARWICKSHIREUNIVERSITYNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="WESTHERTFORDSHIREHOSPITALSNHSTRUST",
        "WESTHERTFORDSHIRETEACHINGHOSPITALSNHSTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="NORTHCUMBRIAUNIVERSITYHOSPITALSNHSTRUST",
        "NORTHCUMBRIAINTEGRATEDCARENHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SOUTHTYNESIDENHSFOUNDATIONTRUST",
        "SOUTHTYNESIDEANDSUNDERLANDNHSFOUNDATIONTRUST",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="CITYHOSPITALSSUNDERLANDNHSFOUNDATIONTRUST",
        "SOUTHTYNESIDEANDSUNDERLANDNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="ABERTAWEBROMORGANNWGUNIVERSITYHEALTHBOARD",
        "CWMTAFMORGANNWGUNIVERSITYHEALTHBOARD",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="SWANSEABAYUNIVERSITYHEALTHBOARD",
        "CWMTAFMORGANNWGUNIVERSITYHEALTHBOARD",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="PORTSMOUTHHOSPITALSNHSTRUST",
        "PORTSMOUTHHOSPITALSUNIVERSITYNHSTRUST",
        data_frame$Trust_name)
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="CWMTAFUNIVERSITYHEALTHBOARD",
        "CWMTAFMORGANNWGUNIVERSITYHEALTHBOARD",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="THEROYALBOURNEMOUTHANDCHRISTCHURCHHOSPITALSNHSFOUNDATION",
        "UNIVERSITYHOSPITALSDORSETNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="POOLEHOSPITALNHSFOUNDATIONTRUST",
        "UNIVERSITYHOSPITALSDORSETNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="BRIGHTONANDSUSSEXUNIVERSITYHOSPITALSNHSTRUST",
        "UNIVERSITYHOSPITALSSUSSEXNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="WESTONAREAHEALTHNHSTRUST",
        "UNIVERSITYHOSPITALSBRISTOLANDWESTONNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="UNIVERSITYHOSPITALSBRISTOLNHSFOUNDATIONTRUST",
        "UNIVERSITYHOSPITALSBRISTOLANDWESTONNHSFOUNDATIONTRUST",
        data_frame$Trust_name)
    
    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="YORKTEACHINGHOSPITALNHSFOUNDATIONTRUST",
        "YORKANDSCARBOROUGHTEACHINGHOSPITALSNHSFOUNDATIONTRUST",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="NHSAYRSHIREARRAN",
        "NHSAYRSHIREANDARRAN",
        data_frame$Trust_name)

    data_frame$Trust_name <-
      ifelse(
        data_frame$Trust_name=="NHSDUMFRIESGALLOWAY",
        "NHSDUMFRIESANDGALLOWAY",
        data_frame$Trust_name)
    
    data_frame$Year <- year_to_add

    assign(df_name, data_frame, envir = .GlobalEnv)

    message(paste("  -> Successfully created dataframe:", df_name))

  }, error = function(e) {
    warning(paste("  -> Skipping file '", file_name_full, "' due to error:", e$message))
  })
}

message("\nConversion complete.")
```

```{r, extract all of our unit names and all of our trust names for checking}
all_NNAP_unit_names <- 
  2017:2023 %>%
  lapply(function(yr) {
    df <- get(paste0("nnap_", yr))
    df %>% select(Unit_name)
  }) %>%
  bind_rows() %>%
  distinct() %>%
  arrange(Unit_name)

all_MBRRACE_trust_names <- 
  2017:2023 %>%
  lapply(function(yr) {
    df <- get(paste0("perinatal_mortality_rates_", yr, "_trusthealth_board"))
    df %>% select(Trust_name)
  }) %>%
  bind_rows() %>%
  distinct() %>%
  arrange(Trust_name)
```

```{r, read in our hospital trust linkage sheet and add necessary suffix duplicates to allow for joining to all possible names}
hospital_trust_manual_linkage_sheet <-
  read.csv("Linking_hospitals_to/hospital_trust_manual_linkage_sheet_master.csv")

levels <- 
  c(
    "_SCU", 
    "_LNU", 
    "_NICU",
    "SCU", 
    "LNU", 
    "NICU",
    "SCBU",
    "1",
    "2",
    "3")

hospital_trust_manual_linkage_sheets <- lapply(levels, function(level) {
  sheet <- hospital_trust_manual_linkage_sheet
  sheet$Unit_name <- paste0(sheet$Unit_name, level)
  return(sheet)
})

names(hospital_trust_manual_linkage_sheets) <- levels

hospital_trust_manual_linkage_sheet_all_levels <- 
  bind_rows(hospital_trust_manual_linkage_sheets)
hospital_trust_manual_linkage_sheet_all_levels <- 
  bind_rows(hospital_trust_manual_linkage_sheet_all_levels, hospital_trust_manual_linkage_sheet)

write.csv(hospital_trust_manual_linkage_sheet_all_levels, "Linking_hospitals_to/hospital_trust_manual_linkage_sheet_all_levels.csv", row.names = F)
```

```{r, check all of our units are matched to an updated trust name}
library(dplyr)
unmatched_units <- list()

for (yr in 2017:2023) {
  nnap_data_for_year <- get(paste0("nnap_", yr))
  
  nnap_data_for_year_with_trust_name <- 
    left_join(
      nnap_data_for_year, 
      hospital_trust_manual_linkage_sheet_all_levels, 
      by = join_by(Unit_name))
  
  print(paste0(yr, ":"))
  print("This year has resulted in this number of hospitals in the NNAP data being duplicated:")
  print(nrow(nnap_data_for_year) - 
          nrow(nnap_data_for_year_with_trust_name))
  
  assign(
    paste0("nnap_", yr, "_with_trust_name"), 
    nnap_data_for_year_with_trust_name, 
    envir = .GlobalEnv)
  
  unmatched <- 
    nnap_data_for_year_with_trust_name %>%
    filter(is.na(Trust_name)) %>%
    select(Unit_name) %>%
    distinct() 
  
  
  unmatched_units[[as.character(yr)]] <- unmatched
  
  diff_rows <- nrow(nnap_data_for_year_with_trust_name) - nrow(nnap_data_for_year)
  
  message("Year ", yr, " → difference = ", diff_rows)
  
  if (diff_rows != 0) {
    # Find problematic Unit_names that cause row duplication
    dup_units <- hospital_trust_manual_linkage_sheet_all_levels %>%
      count(Unit_name) %>%
      filter(n > 1) %>%
      filter(Unit_name %in% df$Unit_name)
    
    if (nrow(dup_units) > 0) {
      message("  Problematic Unit_name(s): ", paste(dup_units$Unit_name, collapse = "; "))
    }
  }
}
```

```{r, list the unmatched units from NNAP for review of the linkage sheet}
unmatched_units_frame <- 
  unique(bind_rows(unmatched_units))

unmatched_units$Trust_name <- NA

unique(unmatched_units$Unit_name)

write.csv(unmatched_units$Unit_name, "Linking_hospitals_to/hospitals_without_trusts_to_assign.csv", row.names=F)
```

```{r, check all the trusts in the MBRRACE data are matched to at least one unit}
all_unmatched_trusts <- bind_rows(
  lapply(2017:2023, function(yr) {
    
    df <- 
      get(paste0(
        "perinatal_mortality_rates_", yr, "_trusthealth_board"))
    
    df %>%
      filter(!Trust_name %in% hospital_trust_manual_linkage_sheet_all_levels$Trust_name) %>%
      distinct(Trust_name) 
  })
    
)

all_unmatched_trusts_frame <- 
  unique(
    bind_rows(
      hospital_trust_manual_linkage_sheet_all_levels, 
      all_unmatched_trusts))

all_unmatched_trusts_frame <- 
  all_unmatched_trusts_frame %>%
  arrange(Trust_name)

write.csv(
  all_unmatched_trusts_frame, 
  "Linking_hospitals_to/hospital_trust_manual_linkage_sheet_to_update.csv", 
  row.names=F)
```


******************************************************************************
Joining MBRRACE data to NNAP data
******************************************************************************

```{r, combine trusts as necessary and tidy the MBRRACE data frame}
for (yr in 2017:2023) {
  
  MBRRACE_data_for_year <- 
    get(paste0("perinatal_mortality_rates_", yr, "_trusthealth_board"))

  cols_to_exclude_from_renaming <- 
    c(
      "ReportYear",
      "OrganisationCode",
      "Trust_name",
      "CountryName",
      "RegionName",
      "SustainabilityAndTransformationPartnershipName",
      "IntegratedCareBoardName",
      "NeonatalNetworkName",
      "Trust_name_original",
      "Year"
    )

all_MBRRACE_data_for_year <-
  left_join(
    MBRRACE_data_for_year,
    by = join_by(
      ReportYear,
      OrganisationCode, 
      Trust_name, 
      CountryName, 
      RegionName,
      SustainabilityAndTransformationPartnershipName,
      IntegratedCareBoardName, 
      NeonatalNetworkName,
      Trust_name_original, 
      Year)
  )

  all_MBRRACE_data_for_year <- all_MBRRACE_data_for_year %>%
    select(-c(
      CrudeStillbirthCategoryName,
      StabilisedStillbirthCategoryName,
      StabilisedStillbirthCI,
      CrudeNeonatalDeathCategoryName,
      StabilisedNeonatalDeathCategoryName,
      StabilisedNeonatalDeathCI,
      CrudePerinatalDeathCategoryName,
      StabilisedPerinatalDeathCategoryName,
      StabilisedPerinatalDeathCI
    ))
  
  columns_to_sum <- 
    c("TotalBirths", 
      "TotalStillbirths", 
      "TotalLiveBirths", 
      "TotalNeonatalDeaths", 
      "TotalPerinatalDeaths")

  columns_to_mean <- 
    c("Longitude", 
      "Latitude", 
      "CrudeStillbirthRate", 
      "CrudeNeonatalDeathRate", 
      "StabilisedStillbirthRate", 
      "StabilisedNeonatalDeathRate", 
      "CrudePerinatalDeathRate", 
      "StabilisedPerinatalDeathRate", 
      "CrudePerinatalDeathRate", 
      "GroupAverageStillbirthRate", 
      "GroupAverageNeonatalDeathRate", 
      "GroupAverageStillbirthRate", 
      "GroupAveragePerinatalDeathRate")

  MBRRACE_data_for_year_trusts_combined <-
    all_MBRRACE_data_for_year %>%
    group_by(CountryName, RegionName, Trust_name) %>%
    summarise(
      ComparatorGroupID = min(ComparatorGroupID, na.rm = T),
      MBRRACE_report_year = first(ReportYear),
      NeonatalNetworkName = paste(unique(NeonatalNetworkName), collapse = "; "),
      OrganisationCode = paste(unique(OrganisationCode), collapse = "; "),
      Trust_name_original = paste(unique(Trust_name_original), collapse = "; "),
      number_of_trusts_combined = length(unique(Trust_name_original)),
      across(all_of(columns_to_mean), ~ mean(.x, na.rm = TRUE), .names = "{.col}"),
      across(all_of(columns_to_sum), ~ sum(.x, na.rm = TRUE), .names = "{.col}"),
      .groups = "drop"
    )
  
MBRRACE_data_for_year_trusts_combined <- 
  MBRRACE_data_for_year_trusts_combined %>%
  mutate(
    ComparatorGroupName = case_when(
      ComparatorGroupID == 1 ~ "Level_3_NICU_and_neonatal_surgery",
      ComparatorGroupID == 2 ~ "Level_3_NICU",
      ComparatorGroupID == 3 ~ "Over_4000_births",
      ComparatorGroupID == 4 ~ "Between_2000_3999_births",
      ComparatorGroupID == 5 ~ "Under_2000_births",
      TRUE ~ NA_character_
    )
  )
  
  assign(
    paste0("MBRRACE_trusts_combined_", yr), 
    MBRRACE_data_for_year_trusts_combined, 
    envir = .GlobalEnv
  )
}


```

```{r}
NNAP_data_with_trust_name_without_unit_level <- data.frame()
NNAP_data_with_trust_name_with_unit_level <- data.frame()

for (yr in 2017:2023) {
  
  NNAP_data_for_year_with_trust_name_with_rows_of_NAs <- 
    get(paste0("nnap_", yr, "_with_trust_name"))
  
  NNAP_data_for_year_with_trust_name <-
    NNAP_data_for_year_with_trust_name_with_rows_of_NAs %>%
  filter(!if_all(everything(), is.na))
  print(paste0(
    "Removed_", 
    nrow(NNAP_data_for_year_with_trust_name_with_rows_of_NAs) - 
      nrow(NNAP_data_for_year_with_trust_name), 
    "_rows with NA in every column"))
  
  NNAP_data_for_year_with_trust_name$Unit_level_number <- 
    as.numeric(NNAP_data_for_year_with_trust_name$Unit_level)
  
  
  NNAP_data_for_year_with_trust_name_without_unit_level <-
    subset(NNAP_data_for_year_with_trust_name, is.na(Unit_level_number))
  if (nrow(NNAP_data_for_year_with_trust_name_without_unit_level)>0){
  NNAP_data_for_year_with_trust_name_without_unit_level$Year <- yr
  }
  
  NNAP_data_with_trust_name_without_unit_level <- 
    bind_rows(NNAP_data_with_trust_name_without_unit_level,
          NNAP_data_for_year_with_trust_name_without_unit_level)           
           
  NNAP_data_for_year_with_trust_name_with_unit_level <-
    subset(NNAP_data_for_year_with_trust_name, !is.na(Unit_level_number))
  NNAP_data_for_year_with_trust_name_with_unit_level$Year <- yr
  
  
  NNAP_data_with_trust_name_with_unit_level <- 
    bind_rows(NNAP_data_with_trust_name_with_unit_level,
          NNAP_data_for_year_with_trust_name_with_unit_level)           
           
  NNAP_data_for_year_by_trust <-
    NNAP_data_for_year_with_trust_name %>%
    filter(!is.na(Trust_name)) %>%
    group_by(Trust_name) %>%
      dplyr::summarise(
        Unit_names = paste(unique(Unit_name), collapse = "; "),
        Unit_levels = paste(unique(Unit_level), collapse = "; "),
        Unit_level_highest = max(Unit_level_number, na.rm=T),
        Year = yr,
        across(
        .cols = where(is.numeric),
        .fns = sum,
        na.rm = FALSE
        )
      )
  NNAP_data_for_year_by_trust$Unit_level_highest_character <-
    as.character(NNAP_data_for_year_by_trust$Unit_level_highest)
 
  assign(
    paste0("NNAP_data_for_", yr, "_by_trust"), 
    NNAP_data_for_year_by_trust, envir = .GlobalEnv)
}

  dir.create("manual_unit_level_definition")      
  
  NNAP_data_with_trust_name_without_unit_level <-
    unique(NNAP_data_with_trust_name_without_unit_level[,c("Unit_name", "Unit_level", "Year")])
  
  NNAP_data_with_trust_name_with_unit_level <-
    unique(NNAP_data_with_trust_name_with_unit_level[,c("Unit_name", "Unit_level", "Year")])
  
  NNAP_data_with_trust_name_with_unit_level <-
    NNAP_data_with_trust_name_with_unit_level[
      order(NNAP_data_with_trust_name_with_unit_level$Unit_name), ]
  
  write.csv(NNAP_data_with_trust_name_without_unit_level,
            "manual_unit_level_definition/NNAP_data_with_trust_name_without_unit_level.csv",
            row.names=F)
  write.csv(NNAP_data_with_trust_name_with_unit_level,
            "manual_unit_level_definition/NNAP_data_with_trust_name_with_unit_level.csv",
            row.names=F)
```

now we have totals by trust, we can calculate percentages for each of our metrics

```{r, calculating percentages of each outcome and pulling out trusts without unit levels}

for (yr in 2017:2023) {
  NNAP_data_for_year_by_trust_with_percent <- 
    get(paste0("NNAP_data_for_", yr, "_by_trust"))
  
library(dplyr)
  
NNAP_data_for_year_by_trust_with_percent <- 
  NNAP_data_for_year_by_trust_with_percent %>%
  mutate(
    
    bpd_crude_pct = if_else(
      (bpd_n_alive_and_yes_bpd + bpd_n_alive_and_no_bpd) == 0,
      NA_real_,
      bpd_n_alive_and_yes_bpd /
        (bpd_n_alive_and_yes_bpd + bpd_n_alive_and_no_bpd) * 100
    ),
    
    NEC_crude_pct = if_else(
      (NEC_n_yes_NEC + NEC_n_no_NEC) == 0,
      NA_real_,
      NEC_n_yes_NEC / (NEC_n_yes_NEC + NEC_n_no_NEC) * 100
    ),
    
    sepsis_crude_pct = if_else(
      (sepsis_n_yes_sepsis + sepsis_n_no_sepsis) == 0,
      NA_real_,
      sepsis_n_yes_sepsis / (sepsis_n_yes_sepsis + sepsis_n_no_sepsis) * 100
    ),
    
    IVH_crude_pct = if_else(
      (IVH_n_yes_IVH + IVH_n_no_IVH) == 0,
      NA_real_,
      IVH_n_yes_IVH / (IVH_n_yes_IVH + IVH_n_no_IVH) * 100
    ),
    
    cPVL_crude_pct = if_else(
      (cPVL_n_yes_cPVL + cPVL_n_no_cPVL) == 0,
      NA_real_,
      cPVL_n_yes_cPVL / (cPVL_n_yes_cPVL + cPVL_n_no_cPVL) * 100
    ),
    
    DCC_crude_pct = if_else(
      (DCC_n_yes_DCC + DCC_n_no_DCC) == 0,
      NA_real_,
      DCC_n_yes_DCC / (DCC_n_yes_DCC + DCC_n_no_DCC) * 100
    ),
    
    ANS_crude_pct = if_else(
      (ANS_n_yes_ANS + ANS_n_no_ANS) == 0,
      NA_real_,
      ANS_n_yes_ANS / (ANS_n_yes_ANS + ANS_n_no_ANS) * 100
    ),
    
    MgSO_crude_pct = if_else(
      (MgSO_n_yes_MgSO + MgSO_n_no_MgSO) == 0,
      NA_real_,
      MgSO_n_yes_MgSO / (MgSO_n_yes_MgSO + MgSO_n_no_MgSO) * 100
    ),
    
    normothermia_crude_pct = if_else(
      (Temperature_n_normothermia_yes + Temperature_n_normothermia_no) == 0,
      NA_real_,
      Temperature_n_normothermia_yes / (Temperature_n_normothermia_yes + Temperature_n_normothermia_no) * 100
    ),
    
    hypothermia_crude_pct = if_else(
      (Temperature_n_normothermia_yes + Temperature_n_normothermia_no) == 0,
      NA_real_,
      Temperature_n_Temperature_low / (Temperature_n_normothermia_yes + Temperature_n_normothermia_no) * 100
    ),
    
    hyperthermia_crude_pct = if_else(
      (Temperature_n_normothermia_yes + Temperature_n_normothermia_no) == 0,
      NA_real_,
      Temperature_n_Temperature_high / (Temperature_n_normothermia_yes + Temperature_n_normothermia_no) * 100
    )
  )
    
  assign(
    paste0("NNAP_data_for_", yr, "_by_trust_with_percent"), 
    NNAP_data_for_year_by_trust_with_percent, envir = .GlobalEnv)
}

```

then we can join in our MBRRACE data, so that we can compare NNAP percentages to MBRRACE outcome figures

```{r, join MBRRACE data to the NNAP data that has been combined into trusts to make NNAP_and_MBRRACE_combined_data_}
all_duplicates <- list()

for (yr in 2017:2023) {
  NNAP_data_for_year <- 
    get(paste0("NNAP_data_for_", yr, "_by_trust_with_percent"))
  
# get the MBRRACE data for that year
  MBRRACE_data_for_year <- 
    get(paste0("MBRRACE_trusts_combined_", yr))
  
  #join the MBRRACE data for that year to the NNAP data
  
  NNAP_and_MBRRACE_combined_data <- 
    left_join(
      NNAP_data_for_year,
      MBRRACE_data_for_year, 
      by = join_by(Trust_name))
  
  #for some reason MBRRACE data has -1 if the rate is missing, we need to change that
  NNAP_and_MBRRACE_combined_data$CrudeStillbirthRate <- 
    ifelse(NNAP_and_MBRRACE_combined_data$CrudeStillbirthRate==-1,
           NA,
           NNAP_and_MBRRACE_combined_data$CrudeStillbirthRate)
  NNAP_and_MBRRACE_combined_data$CrudeNeonatalDeathRate <- 
    ifelse(NNAP_and_MBRRACE_combined_data$CrudeNeonatalDeathRate==-1,
           NA,
           NNAP_and_MBRRACE_combined_data$CrudeNeonatalDeathRate)
  NNAP_and_MBRRACE_combined_data$CrudePerinatalDeathRate <- 
    ifelse(NNAP_and_MBRRACE_combined_data$CrudePerinatalDeathRate==-1,
           NA,
           NNAP_and_MBRRACE_combined_data$CrudePerinatalDeathRate)
  
  #extract the standardisation factor
  
  #print check that we haven't had a many to many join
  print("This number should be zero, otherwise multiple trusts are getting joined to the same unit")
  print(nrow(NNAP_data_for_year) - nrow(NNAP_and_MBRRACE_combined_data))
  print("This is the number of trusts for which we have MBRRACE data but no NNAP data in this year:")
  print(nrow(MBRRACE_data_for_year) - nrow(NNAP_and_MBRRACE_combined_data))
  
  #assign the data back to the environment
  assign(
    paste0("NNAP_and_MBRRACE_combined_data_", yr), 
    NNAP_and_MBRRACE_combined_data, envir = .GlobalEnv)
  
  
  cat("Number of rows in combined_data_", yr, ": ", nrow(NNAP_and_MBRRACE_combined_data), "\n", sep = "")
  
  # check for duplicated Unit_names
  duplicated_units <- 
    NNAP_and_MBRRACE_combined_data %>%
    group_by(Unit_names) %>%
    filter(n() > 1) %>%
    distinct(Unit_names)
  
  if (nrow(duplicated_units) > 0) {
  all_duplicates[[as.character(yr)]] <- NNAP_and_MBRRACE_combined_data %>%
    filter(Unit_names %in% duplicated_units$Unit_names) %>%
    select(Unit_names, Trust_name)
}
  
if (nrow(duplicated_units) > 0) {
  cat("Duplicated Unit_name(s) in combined_data_", yr, " with corresponding Trust_name(s):\n", sep = "")
  NNAP_and_MBRRACE_combined_data %>%
    filter(Unit_names %in% duplicated_units$Unit_names) %>%
    select(Unit_names, Trust_name) %>%
    arrange(Unit_names) %>%
    print()
    cat("There are duplicated Unit_names in NNAP_and_MBRRACE_combined_data for ", yr, "\n MAKE SURE YOU CHECK THEM \n", sep = "")
    cat("\n")
    
} else {
  cat("No duplicated Unit_names in combined_data_", yr, "\n", sep = "")
  cat("\n")
}

    # check for duplicated Trust_name
  duplicated_trusts <- 
    NNAP_and_MBRRACE_combined_data %>%
    group_by(Trust_name) %>%
    filter(n() > 1) %>%
    distinct(Trust_name)
  
  if (nrow(duplicated_trusts) > 0) {
  all_duplicates[[as.character(yr)]] <- NNAP_and_MBRRACE_combined_data %>%
    filter(Trust_name %in% duplicated_trusts$Trust_name) %>%
    select(Unit_names, Trust_name)
}
  
if (nrow(duplicated_trusts) > 0) {
  cat("Duplicated Trust_name(s) in combined_data_", yr, " with corresponding Trust_name(s):\n", sep = "")
  NNAP_and_MBRRACE_combined_data %>%
    filter(Trust_name %in% duplicated_trusts$Trust_name) %>%
    select(Unit_names, Trust_name) %>%
    arrange(Trust_name) %>%
    print()
    cat("There are duplicated Trust_name in NNAP_and_MBRRACE_combined_data for ", yr, "\n MAKE SURE YOU CHECK THEM \n", sep = "")
    cat("\n")
    
} else {
  cat("No duplicated Trust_name in combined_data_", yr, "\n", sep = "")
  cat("\n")
}
  
}

all_duplicates_df <- bind_rows(all_duplicates, .id = "Year")


```


```{r, combine all of the years worth of data}

NNAP_and_MBRRACE_all_years <- 
  bind_rows(lapply(2017:2023, function(yr) {
    get(paste0("NNAP_and_MBRRACE_combined_data_", yr))
  }))
```

```{r}
cols <- 
  c("TotalStillbirths", 
    "TotalPerinatalDeaths",
    "TotalLiveBirths", 
    "TotalNeonatalDeaths")

NNAP_and_MBRRACE_all_years[cols] <- 
  lapply(NNAP_and_MBRRACE_all_years[cols], function(x) ifelse(x %in% c(-1, -2), NA, x))
```

```{r}
NNAP_and_MBRRACE_trusts_with_no_unit_level <-
  subset(NNAP_and_MBRRACE_all_years, (grepl(x=Unit_levels, pattern="NA")))

dir.create("manual_unit_level_definition")
write.csv(
  NNAP_and_MBRRACE_trusts_with_no_unit_level, 
  "manual_unit_level_definition/NNAP_and_MBRRACE_trusts_with_no_unit_level.csv")
print("This should hopefully now be none. Here I am at a check point, what does the following say- it should say zero, otherwise you may need to add the level of some units to the manual_unit_level_definition file:")
length(NNAP_and_MBRRACE_trusts_with_no_unit_level$Trust_name)
```


```{r, for each of the steroid variables, I want to separate them depending on how they are distributed into before and after end of 2021}
columns <- c(
  "ANS_n_alive_and_dead_eligible",
  "ANS_n_yes_ANS",
  "ANS_n_no_ANS",
  "ANS_n_missing_ANS_data",
  "ANS_crude_pct"
)

for (v in columns) {

  NNAP_and_MBRRACE_all_years[[paste0(v, "_up_to_21")]] <-
    ifelse(NNAP_and_MBRRACE_all_years$Year <= 2021,
           NNAP_and_MBRRACE_all_years[[v]],
           NA)

  NNAP_and_MBRRACE_all_years[[paste0(v, "_after_21")]] <-
    ifelse(NNAP_and_MBRRACE_all_years$Year >= 2022,
           NNAP_and_MBRRACE_all_years[[v]],
           NA)
}
```

```{r, create columns that have turned zero rates into NA}
  columns_to_remove_zeros  = 
    c("StabilisedNeonatalDeathRate",
      "StabilisedNeonatalDeathRate_ex_anoms",
      "CrudeNeonatalDeathRate",
      "CrudeNeonatalDeathRate_ex_anoms",
      "bpd_crude_pct", 
      "NEC_crude_pct",
      "sepsis_crude_pct",
      "IVH_crude_pct",
      "cPVL_crude_pct",
      "hypothermia_crude_pct",
      "hyperthermia_crude_pct",
      "normothermia_crude_pct",
      "DCC_crude_pct",
      "ANS_crude_pct",
      "ANS_crude_pct_up_to_21",
      "ANS_crude_pct_after_21",
      "MgSO_crude_pct")

for (col in columns_to_remove_zeros) {
  new_col <- paste0(col, "_no_zeros")
  
  NNAP_and_MBRRACE_all_years[[new_col]] <- 
    ifelse(NNAP_and_MBRRACE_all_years[[col]] == 0, NA, NNAP_and_MBRRACE_all_years[[col]])
}
```

```{r, function to rank both low and high being good}
library(dplyr)

rank_vars <- 
  function(
    data, 
    low_is_good, 
    high_is_good, 
    group_var = "Year") {

  data %>%
    group_by(.data[[group_var]]) %>%
    mutate(
      # LOW → HIGH ranks, NAs stay NA
      across(all_of(low_is_good),
             ~ ifelse(is.na(.x), NA, rank(.x, ties.method = "min")),
             .names = "{.col}_rank"),
      # HIGH → LOW ranks, NAs stay NA
      across(all_of(high_is_good),
             ~ ifelse(is.na(.x), NA, rank(-.x, ties.method = "min")),
             .names = "{.col}_rank")
    ) %>%
    ungroup()
}
```

```{r, create a function to rank variables with no ties using alphabetical order for any ranks for purposes of a table}
library(dplyr)
library(purrr)

rank_vars_no_ties <- 
  function(
    data, 
    low_is_good, 
    high_is_good, 
    trust_var = "Trust_name",
    group_var = "Year") {

  # LOW is good
  for (v in low_is_good) {
    data <- data %>%
      group_by(.data[[group_var]]) %>%
      arrange(.data[[v]], .data[[trust_var]], .by_group = TRUE) %>%
      mutate(
        "{v}_no_ties" := ifelse(
          is.na(.data[[v]]),
          NA_integer_,
          row_number()
        )
      ) %>%
      ungroup()
  }

  # HIGH is good
  for (v in high_is_good) {
    data <- data %>%
      group_by(.data[[group_var]]) %>%
      arrange(desc(.data[[v]]), .data[[trust_var]], .by_group = TRUE) %>%
      mutate(
        "{v}_no_ties" := ifelse(
          is.na(.data[[v]]),
          NA_integer_,
          row_number()
        )
      ) %>%
      ungroup()
  }

  data
}
```

```{r, set variables for low is good}
low_is_good_variables <-
  c(
    "StabilisedNeonatalDeathRate",
    "StabilisedNeonatalDeathRate_no_zeros",
    "StabilisedNeonatalDeathRate_ex_anoms",
    "StabilisedNeonatalDeathRate_ex_anoms_no_zeros",
    "CrudeNeonatalDeathRate",
    "CrudeNeonatalDeathRate_no_zeros",
    "CrudeNeonatalDeathRate_ex_anoms",
    "CrudeNeonatalDeathRate_ex_anoms_no_zeros",
    "bpd_crude_pct", 
    "NEC_crude_pct",
    "sepsis_crude_pct",
    "IVH_crude_pct",
    "cPVL_crude_pct",
    "hypothermia_crude_pct",
    "hyperthermia_crude_pct",
    "bpd_crude_pct_no_zeros", 
    "NEC_crude_pct_no_zeros",
    "sepsis_crude_pct_no_zeros",
    "IVH_crude_pct_no_zeros",
    "cPVL_crude_pct_no_zeros",
    "hypothermia_crude_pct_no_zeros",
    "hyperthermia_crude_pct_no_zeros")
```

```{r, set variables for high is good}
high_is_good_variables <- 
  c("normothermia_crude_pct",
    "DCC_crude_pct",
    "ANS_crude_pct",
    "ANS_crude_pct_up_to_21",
    "ANS_crude_pct_after_21",
    "MgSO_crude_pct",
    "normothermia_crude_pct_no_zeros",
    "DCC_crude_pct_no_zeros",
    "ANS_crude_pct_no_zeros",
    "ANS_crude_pct_up_to_21_no_zeros",
    "ANS_crude_pct_after_21_no_zeros",
    "MgSO_crude_pct_no_zeros")
```

```{r, create a separate column that tells us when the rank is tied so we can mark this in the table if we want}
#helper function
flag_ties <- function(data, vars, group_var = "Year") {
  data %>%
    group_by(.data[[group_var]]) %>%
    mutate(
      across(
        all_of(vars),
        ~ ifelse(
          is.na(.x),
          NA_integer_,
          ave(.x, .x, FUN = length) > 1
        ) |> as.integer(),
        .names = "{.col}_is_tied"
      )
    ) %>%
    ungroup()
}

NNAP_and_MBRRACE_all_years_ranked <-
  flag_ties(
    data = NNAP_and_MBRRACE_all_years,
    vars = low_is_good_variables,
    group_var = "Year"
  )

```

```{r, run our ranking function through the data to get a rank with ties}
NNAP_and_MBRRACE_all_years_ranked <- rank_vars(
  data = NNAP_and_MBRRACE_all_years,
  
  low_is_good  = 
    low_is_good_variables,
  
  high_is_good = 
    high_is_good_variables,
  
  group_var = "Year"
)
```

```{r}
library(dplyr)
NNAP_and_MBRRACE_all_years_ranked <- 
  NNAP_and_MBRRACE_all_years_ranked %>%
    group_by(Year) %>%
  mutate(
    across(
      ends_with("_rank"),
      ~ ifelse(is.na(.x), NA, (.x - min(.x, na.rm = TRUE)) / 
                              (max(.x, na.rm = TRUE) - min(.x, na.rm = TRUE))),
      .names = "{.col}_norm"
    ) %>%
    ungroup()
  )
```

```{r, create average rankings}
library(dplyr)
NNAP_and_MBRRACE_all_years_ranked$mean_perinatal_rank_norm <-
  rowMeans(
    NNAP_and_MBRRACE_all_years_ranked[, c(
      "normothermia_crude_pct_rank_norm",
      "DCC_crude_pct_rank_norm",
      "ANS_crude_pct_rank_norm",
      "MgSO_crude_pct_rank_norm"
    )],
    na.rm = TRUE
  )

NNAP_and_MBRRACE_all_years_ranked$mean_morbidity_rank_norm <-
  rowMeans(
    NNAP_and_MBRRACE_all_years_ranked[, c(
            "bpd_crude_pct_rank_norm", 
            "NEC_crude_pct_rank_norm",
            "sepsis_crude_pct_no_zeros_rank_norm",
            "IVH_crude_pct_rank_norm",
            "cPVL_crude_pct_rank_norm"
    )],
    na.rm = TRUE
  )

NNAP_and_MBRRACE_all_years_ranked$mean_of_perinatal_and_morbidity_rank_norm <-
  rowMeans(
    NNAP_and_MBRRACE_all_years_ranked[, c(
            "mean_perinatal_rank_norm", 
            "mean_morbidity_rank_norm"
    )],
    na.rm = TRUE
  )

NNAP_and_MBRRACE_all_years_ranked$mean_rank_norm <-
  rowMeans(
    NNAP_and_MBRRACE_all_years_ranked[, c(
            "bpd_crude_pct_rank_norm", 
            "NEC_crude_pct_rank_norm",
            "sepsis_crude_pct_no_zeros_rank_norm",
            "IVH_crude_pct_rank_norm",
            "cPVL_crude_pct_rank_norm",
            "normothermia_crude_pct_rank_norm",
            "DCC_crude_pct_rank_norm",
            "ANS_crude_pct_rank_norm",
            "MgSO_crude_pct_rank_norm"
    )],
    na.rm = TRUE
  )
```

```{r}
low_is_good_variables <-
  append(
    low_is_good_variables,
    c(
      "mean_rank_norm",
      "mean_perinatal_rank_norm",
      "mean_morbidity_rank_norm",
      "mean_of_perinatal_and_morbidity_rank_norm"
    )
  )
```

```{r, run our ranking function through the data to get a rank without any ties for the purposes of a wide table}
NNAP_and_MBRRACE_all_years_ranked <- rank_vars_no_ties(
  data = NNAP_and_MBRRACE_all_years_ranked,
  
  low_is_good  = 
    low_is_good_variables,
  
  high_is_good = 
    high_is_good_variables,
  
  trust_var = "Trust_name",
  
  group_var = "Year"
)
```

```{r, reorder columns to create NNAP_and_MBRRACE_data_to_analyse}
library(dplyr)

NNAP_and_MBRRACE_data_to_analyse <-
  NNAP_and_MBRRACE_all_years_ranked %>%
  dplyr::select(
    Trust_name,
    Year,

    starts_with("Unit_level_highest"),

    starts_with("mean_"),
    starts_with("StabilisedNeonatalDeathRate"),
    starts_with("CrudeNeonatalDeathRate"),
    starts_with("bpd_crude_pct"),
    starts_with("NEC_crude_pct"),
    starts_with("sepsis_crude_pct"),
    starts_with("IVH_crude_pct"),
    starts_with("cPVL_crude_pct"),
    starts_with("hypothermia_crude_pct"),
    starts_with("hyperthermia_crude_pct"),
    starts_with("normothermia_crude_pct"),
    starts_with("DCC_crude_pct"),
    starts_with("ANS_crude_pct"),
    starts_with("MgSO_crude_pct")
  )
write.csv(NNAP_and_MBRRACE_data_to_analyse, "combined_data_to_loa/NNAP_and_MBRRACE_data_to_analyse.csv", row.names=F)
```

```{r, separate our reordered frames into years just for purposes of checking easily}
NNAP_and_MBRRACE_data_to_check_2017 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2017)
NNAP_and_MBRRACE_data_to_check_2018 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2018)
NNAP_and_MBRRACE_data_to_check_2019 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2019)
NNAP_and_MBRRACE_data_to_check_2020 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2020)
NNAP_and_MBRRACE_data_to_check_2021 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2021)
NNAP_and_MBRRACE_data_to_check_2022 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2022)
NNAP_and_MBRRACE_data_to_check_2023 <-
  NNAP_and_MBRRACE_data_to_analyse %>%
  filter(Year==2023)
```

```{r, simplify our ranks to deciles}
predictors_to_decile <- 
  c(
    "StabilisedNeonatalDeathRate_rank_norm",
    "StabilisedNeonatalDeathRate_ex_anoms_rank_norm",
    
    "mean_rank_norm", 
    "mean_perinatal_rank_norm", 
    "mean_morbidity_rank_norm", 
    
    "ANS_crude_pct_rank_norm", 
    "MgSO_crude_pct_rank_norm", 
    "DCC_crude_pct_rank_norm",
    "normothermia_crude_pct_rank_norm",
    
    "bpd_crude_pct_rank_norm",
    "NEC_crude_pct_rank_norm",
    "sepsis_crude_pct_no_zeros_rank_norm",
    "IVH_crude_pct_rank_norm",
    "cPVL_crude_pct_rank_norm"
    )

desired_deciles <- 10
break_points <- seq(0, 1, length.out = desired_deciles + 1)  # 0.0, 0.1, ..., 1.0

for(pred in predictors_to_decile){
  binned_name <- paste0(pred, "_decile")
  
  NNAP[[binned_name]] <- cut(
    NNAP[[pred]],
    breaks = break_points,
    include.lowest = TRUE,
    labels = 1:desired_deciles
  )
  
  NNAP[[binned_name]] <- as.integer(as.character(NNAP[[binned_name]]))
  
  cat(pred, ": created", length(unique(NNAP[[binned_name]])), "bins\n")
}
```

************
cumulative ordinal logistic regression models
*****************************************************************************************************************************************

```{r, predict death from perinatal factors with 10 bins WITHOUT UNIT LEVEL}
library(brms)

brms_decile_model_without_unit_level <- brm(
  StabilisedNeonatalDeathRate_ex_anoms_rank_norm_decile ~ 
    mean_rank_norm_decile +
    (1 | Trust_name) ,
  
  data = NNAP,
  family = cumulative("logit"),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.95, max_treedepth = 15)
)

summary(brms_decile_model_without_unit_level)
brms_decile_model_without_unit_level_death_on_mean_rank_predictors_trust_rank <- brms_decile_model
```


```{r, predict death from perinatal factors with unit level}
library(brms)

brms_decile_model <- brm(
  StabilisedNeonatalDeathRate_ex_anoms_rank_norm_decile ~ 
    mean_rank_norm_decile +
    Unit_level_highest +
    (1 | Trust_name) ,
  
  data = NNAP,
  family = cumulative("logit"),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.95, max_treedepth = 15)
)

summary(brms_decile_model)
brms_decile_model_death_on_mean_rank_predictors_trust_rank <- brms_decile_model
```

```{r, extract a word file from our model }
for (decimal_places in c(1, 2, 3)){

library(flextable)
library(officer)
library(dplyr)
library(tidyr)
library(tibble)

global_table <- NULL
max_rows <- 0
table_list <- list()

pad_rows <- function(df, target_rows) {
  n_missing <- target_rows - nrow(df)
  if(n_missing > 0){
    empty_rows <- df[rep(NA, n_missing), ]
    rownames(empty_rows) <- NULL
    df <- rbind(df, empty_rows)
  }
  return(df)
}

for (name_of_model_to_extract in c(
  "brms_decile_model_death_on_everything_trust_rank",
  "brms_decile_model_death_on_everything_parsimonious_trust_rank",
  "brms_decile_model_death_on_perinatal_predictors_trust_rank",
  "brms_decile_model_death_on_perinatal_predictors_parsimonious_trust_rank",
  "brms_decile_model_death_on_mean_rank_predictors_trust_rank"
  )){
model_to_extract <- get(name_of_model_to_extract)
summary_of_model <- summary(model_to_extract)

if (grepl("NEC", name_of_model_to_extract)) {
  outcome_variable <- "NEC"
} else if (grepl("bpd", name_of_model_to_extract)) {
  outcome_variable <- "bpd"
} else if (grepl("IVH", name_of_model_to_extract)) {
  outcome_variable <- "IVH"
} else if (grepl("cPVL", name_of_model_to_extract)) {
  outcome_variable <- "cPVL"
} else if (grepl("sepsis", name_of_model_to_extract)) {
  outcome_variable <- "sepsis"
} else {
  outcome_variable <- "death"  # fallback if no match
}

coefficients <- rownames_to_column(as.data.frame(fixef(model_to_extract)), var="Predictor")

random_sd <- (VarCorr(model_to_extract)$Trust_name$sd)

random_sd_for_table <- 
  paste0(round(random_sd[1], decimal_places), 
    " (", 
       round(random_sd[3], decimal_places),
    " to ", 
       round(random_sd[4], decimal_places),
    ")")

number_observations <- nobs(model_to_extract)

number_trusts <- as.numeric(summary_of_model$ngrps)

raw_coefficients_to_print <- 
  data.frame(
  
  Predictor= as.character(coefficients$Predictor),
  
  Estimate = paste0(
    round(coefficients$Estimate, decimal_places),
    " (", 
    round(coefficients$Q2.5, decimal_places),
    " to ", 
    round(coefficients$Q97.5, decimal_places),
    ")"
  ),
  
  Odds_ratios = paste0(
    round(exp(coefficients$Estimate), decimal_places),
    " (", 
    round(exp(coefficients$Q2.5), decimal_places),
    " to ", 
    round(exp(coefficients$Q97.5), decimal_places),
    ")"
  )
)

raw_coefficients_to_print <- 
  raw_coefficients_to_print %>% add_row(Predictor = " ", Estimate = " ", Odds_ratios = " ", .before = 1)

raw_coefficients_to_print <- 
  raw_coefficients_to_print %>% add_row(Predictor = "Outcome", Estimate = outcome_variable, Odds_ratios = outcome_variable, .before = 1)

raw_coefficients_to_print <- 
  raw_coefficients_to_print %>% add_row(Predictor = " ", Estimate = " ", Odds_ratios = " ")

raw_coefficients_to_print <- 
  raw_coefficients_to_print %>% add_row(Predictor = "Number of observations", Estimate = as.character(number_observations), Odds_ratios = as.character(number_observations))

raw_coefficients_to_print <- 
  raw_coefficients_to_print %>% add_row(Predictor = "Number of trusts", Estimate = as.character(number_trusts), Odds_ratios = as.character(number_trusts))

raw_coefficients_to_print <- 
  raw_coefficients_to_print %>% add_row(Predictor = "SD of random intercepts", Estimate = as.character(random_sd_for_table), Odds_ratios = as.character(random_sd_for_table))

  max_rows <- max(max_rows, nrow(raw_coefficients_to_print))
  
  table_list[[name_of_model_to_extract]] <- raw_coefficients_to_print

ft <- flextable(raw_coefficients_to_print)

ft <- ft %>%
  theme_vanilla() %>%
  align(align = "center", part = "header") %>%
  autofit()

centered_paragraph <- 
  fp_par(text.align = "center")
font_properties <- fp_text(font.size = 14, bold = TRUE, color = "black")
doc <- 
  read_docx() %>%
  body_add_flextable(ft) 
  
  dir.create("word_tables", showWarnings = F)
  
print(doc, 
      target = paste0("word_tables/", name_of_model_to_extract, "_", decimal_places, "dp", ".docx"))

}}
```

************
cumulative ordinal logistic multivariable regression models
*************

```{r, predict different outcomes from perinatal factors with 10 bins}
library(brms)
#change the outcome as required
brms_decile_model <- brm(
#  StabilisedNeonatalDeathRate_rank_norm_decile ~ 
#  bpd_crude_pct_rank_norm_decile ~ 
  NEC_crude_pct_rank_norm_decile ~ 
#  sepsis_crude_pct_no_zeros_rank_norm_decile ~ 
#  IVH_crude_pct_rank_norm_decile ~ 
#  cPVL_crude_pct_rank_norm_decile ~ 
    
    ANS_crude_pct_rank_norm_decile +
    MgSO_crude_pct_rank_norm_decile +
    normothermia_crude_pct_rank_norm_decile +
    DCC_crude_pct_rank_norm_decile +
  
    Unit_level_highest +
    (1 | Trust_name) ,
  
  data = NNAP,
  family = cumulative("logit"),
  chains = 4,
  cores = 4,
  iter = 4000,
  control = list(adapt_delta = 0.95, max_treedepth = 15)
)

summary(brms_decile_model)
brms_decile_model_NEC_on_perinatal_predictors_norm_decile_rank_level <- brms_decile_model 
```

```{r, parameters for all plots}
alpha_for_histograms <- 0.5
alpha_for_regression_points <- 0.2
alpha_for_regression_line <- 0.5
linewidth_for_histograms <- 0.1
colour_for_loess_regression_line <- "darkorange"
colour_for_straight_regression_line <- "grey30"
dir.create("histograms")
dir.create("basic_regression_plots")
```

```{r, figure 1}
library(ggplot2)
box_plot <-
ggplot(NNAP_and_MBRRACE_data_to_analyse,
       aes(x = Unit_level_highest_character,
           y = StabilisedNeonatalDeathRate_rank_norm,
           fill = factor(Year))) +
  geom_boxplot(
    position = position_dodge(width = 0.8), 
    outlier.shape=NA, coef=Inf, #this doesn't use outlier dots, it just uses the range of data
    lwd=0.2) +  # dodge to separate years
  labs(
    x = "Unit Level",
    y = "Stabilised Neonatal Death Rate (rank norm)",
    fill = "Year"
  ) +
  scale_y_continuous(
  limits = c(0.0, 1.0),
  breaks = seq(0.0, 1.0, by = 0.1)
) +
  coord_cartesian(ylim = c(0,1)) +
  scale_fill_manual(values = c(
  "2017" = "Orange",
  "2018" = "SkyBlue",
  "2019" = "#009E73", ##009E73 is blueish green
  "2020" = "#F0E442", #yellow #F0E442
  "2021" = "#0072B2", #blue #0072B2
  "2022" = "#D55E00", ##D55E00 vermillion
  "2023" = "#000000" #black
  )) +
  theme_minimal() +
  theme(axis.text.x = 
          element_text(
            angle = 0, 
            hjust = 1),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
        )
box_plot

ggsave(filename = paste0(
  "boxplot_mortality",
  ".png"),
         path = "histograms",
         plot = box_plot + 
    theme(axis.title=element_blank(), 
         plot.title=element_blank(), 
         plot.subtitle=element_blank()),,
         device = "png",
         width = 6,
         height = 3,
         limitsize = FALSE,
  bg = "white")
```

***************
loop in colour histograms
***************

```{r, dynamic histogram  colour}
NNAP_and_MBRRACE_data_to_analyse$Year <- 
  as.character(NNAP_and_MBRRACE_data_to_analyse$Year)

for (type in c(
  "crude",
  "rank"
)){
  
for (x_variable in c(
  "normothermia_crude_pct",
  "hypothermia_crude_pct",
  "hyperthermia_crude_pct",
  "StabilisedNeonatalDeathRate",
  "StabilisedNeonatalDeathRate_ex_anoms",
  "ANS_crude_pct",
  "MgSO_crude_pct",
  "bpd_crude_pct",
  "DCC_crude_pct",
  "NEC_crude_pct",
  "NEC_crude_pct_no_zeros",
  "sepsis_crude_pct",
  "sepsis_crude_pct_no_zeros",
  "IVH_crude_pct",
  "IVH_crude_pct_no_zeros",
  "cPVL_crude_pct",
  "cPVL_crude_pct_no_zeros"
)){

flexible_bin_width <- 0.5

if (type=="rank"){
  flexible_bin_width <- 0.01
  x_variable <- paste0(x_variable, "_rank_norm")
}
if (x_variable=="sepsis_crude_pct_no_zeros" | 
    x_variable=="IVH_crude_pct" | 
    x_variable=="StabilisedNeonatalDeathRate" | 
    x_variable=="StabilisedNeonatalDeathRate_ex_anoms"){
  flexible_bin_width <- 0.1
}
  
histogram_loop <-
  ggplot(
      data = NNAP_and_MBRRACE_data_to_analyse, 
      aes(x = !!sym(x_variable), fill=Year)) +
    geom_histogram(
      binwidth = flexible_bin_width, 
      linewidth = linewidth_for_histograms,
      color = "white",
      alpha = 1,
      fill="white") +
  geom_histogram(
      binwidth = flexible_bin_width, 
      linewidth = linewidth_for_histograms,
      color = "white",
      alpha = alpha_for_histograms) +
  labs(title=x_variable) +
  scale_fill_manual(values = c(
  "2017" = "Orange",
  "2018" = "SkyBlue",
  "2019" = "#009E73", ##009E73 is blueish green
  "2020" = "#F0E442", #yellow #F0E442
  "2021" = "#0072B2", #blue #0072B2
  "2022" = "#D55E00", ##D55E00 vermillion
  "2023" = "#000000" #black
  )) +
  theme_minimal() 
histogram_loop

ggsave(filename = paste0(
  x_variable,
  ".png"),
         path = "histograms",
         plot = histogram_loop,
         device = "png",
         width = 6,
         height = 3,
         limitsize = FALSE,
  bg = "white")

ggsave(filename = paste0(
  x_variable,
  "_blank.png"),
         path = "histograms",
         plot = histogram_loop +
    theme(axis.title=element_blank(), 
         plot.title=element_blank(), 
         plot.subtitle=element_blank()),
         device = "png",
         width = 6,
         height = 3,
         limitsize = FALSE,
  bg = "white")

}}

```

```{r, regression plots}
for(death_outcome in c(
  "percentage_total",
  "rank_total")){
y_axis <- "y"
if (death_outcome=="percentage_total"){
  y_axis <- "Stabilised death rate (solid), crude death rate (dashed) %"
  y_variable_stabilised <- "StabilisedNeonatalDeathRate"
  y_variable_crude <- "CrudeNeonatalDeathRate"
}
if (death_outcome=="rank_total"){
  y_axis <- "Stabilised death RANK (solid), crude death RANK (dashed)"
  y_variable_stabilised <- "StabilisedNeonatalDeathRate_rank_norm"
  y_variable_crude <- "CrudeNeonatalDeathRate_rank_norm"
}

for (predictor in c(
  "normothermia",
  "hypothermia",
  "hyperthermia",
  "ANS",
  "MgSO",
  "bpd",
  "NEC",
  "sepsis",
  "IVH",
  "cPVL"
)){

for (type_of_x_variable in c(
  "crude_pct",
  "crude_pct_rank_norm"
))
  
x_axis <- "x"
if (predictor=="normothermia_crude_pct"){
  x_axis <- paste0("Percentage admitted with normothermia ", type_of_x_variable)
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="ANS_crude_pct"){
  x_axis <- "Percentage received antenatal steroids"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="MgSO_crude_pct"){
  x_axis <- "Percentage received magnesium sulphate"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="hypothermia_crude_pct"){
  x_axis <- "Percentage admitted hypOthermic"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="hyperthermia_crude_pct"){
  x_axis <- "Percentage admitted hypERthermic"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="bpd_crude_pct"){
  x_axis <- "Percentage bronchopulmonary dysplasia"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="NEC_crude_pct"){
  x_axis <- "Percentage NEC"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="sepsis_crude_pct"){
  x_axis <- "Percentage sepsis"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="IVH_crude_pct"){
  x_axis <- "Percentage IVH"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}
if (predictor=="cPVL_crude_pct"){
  x_axis <- "Percentage cPVL"
  x_variable <- pasteo(predictor, "_", type_of_x_variable)
}

regression_plot <-
  ggplot(
      data=NNAP_and_MBRRACE_data_to_analyse, 
      aes(x = !!sym(x_variable), y = !!sym(y_variable_stabilised))
    ) +
  geom_point(
    aes(),
      colour = "white",
      alpha=alpha_for_regression_points) +
  geom_point(
    aes(
      colour = Year),
      alpha=alpha_for_regression_points) +
  geom_smooth(
    method = "loess", 
    se = F, 
    colour = colour_for_loess_regression_line, 
    alpha = alpha_for_regression_line
    ) +
  geom_smooth(
    aes(y=!!sym(y_variable_crude)),
    method = "loess", 
    se = F, 
    colour = colour_for_loess_regression_line, 
    alpha = alpha_for_regression_line,
    linetype="dashed"
    ) +
  geom_smooth(
    method = "lm", 
    formula = y ~ x, 
    se = F, 
    colour= colour_for_straight_regression_line, 
    alpha = alpha_for_regression_line) +
  geom_smooth(
    aes(y=!!sym(y_variable_crude)),
    method = "lm", 
    formula = y ~ x, 
    se = F, 
    colour= colour_for_straight_regression_line, 
    alpha = alpha_for_regression_line,
    linetype="dashed") +
  labs(
    x=x_axis,
    y=y_axis,
    title=y_axis) +
  coord_cartesian(
    xlim=c(0, 100)) +
  scale_x_continuous(breaks=seq(0,100, by=10)) +
    theme_minimal() 

print(regression_plot)

ggsave(filename = paste0(
  "regression_",
  x_variable,
  "_",
  death_outcome,
  ".png"),
  path = "basic_regression_plots",
  plot = regression_plot ,
  device = "png",
  width = 6,
  height = 3,
  limitsize = FALSE,
  bg = "white")
}}
```

************************************************************************************
Multilevel illustrative model for paper and summary statistics
***************************************************************************************************************

```{r, give me summary statistics}
years <- 2017:2023
cols  <- 
  c(
    "StabilisedNeonatalDeathRate", 
    "ANS_crude_pct", 
    "MgSO_crude_pct", 
    "normothermia_crude_pct", 
    "DCC_crude_pct", 
    "bpd_crude_pct", 
    "NEC_crude_pct", 
    "sepsis_crude_pct", 
    "IVH_crude_pct", 
    "cPVL_crude_pct")  
summary_statistics <- data.frame(variable = cols, stringsAsFactors = FALSE)

for (yr in years) {

  df <- get(paste0("NNAP_and_MBRRACE_data_to_check_", yr))

  summaries <- sapply(cols, function(col) {
    x <- df[[col]]
    sprintf("%.1f\n(%.1f to %.1f)\nn = %d",
            median(x, na.rm = TRUE),
            quantile(x, 0.25, na.rm = TRUE),
            quantile(x, 0.75, na.rm = TRUE),
            sum(!is.na(x)))
  })

  summary_statistics[[as.character(yr)]] <- summaries
}

summary_statistics
dir.create("summary_statistics")
write.csv(summary_statistics, "summary_statistics/summary_statistics_table_1.csv")
```

```{r, lower part of table 1}
years <- 2017:2023
levels_ordered <- c("1", "2", "3")   # forced order

unit_level_statistics <- data.frame(
  Unit_level_highest_character = levels_ordered,
  stringsAsFactors = FALSE
)

for (yr in years) {

  df <- get(paste0("NNAP_and_MBRRACE_data_to_check_", yr))

  # restrict to rows with stabilised rate available
  df_filtered <- df[!is.na(df$StabilisedNeonatalDeathRate), ]

  # tabulate unit levels
  tab <- table(df_filtered$Unit_level_highest_character)

  # force ordering; missing levels become 0
  year_counts <- sapply(levels_ordered, function(lvl) {
    if (lvl %in% names(tab)) tab[[lvl]] else 0
  })

  unit_level_statistics[[as.character(yr)]] <- year_counts
}

unit_level_statistics

write.csv(unit_level_statistics, "summary_statistics/unit_level_statistics_table_1.csv")
```



```{r, table 2 overall mortality on overall rank multilevel illustrative model draft 1 no interaction on unit parallel lines}
library(lme4)
library(lmerTest)
library(ggplot2)
library(broom.mixed)
library(dplyr)
library(performance)

model_1 <- 
  lmer(
    StabilisedNeonatalDeathRate_rank_norm ~ 
                    mean_rank_norm +
                    Unit_level_highest_character +
                    (1 | Trust_name)  ,
    data=NNAP_and_MBRRACE_data_to_analyse)

dir.create("model_outputs", showWarnings = FALSE)
confidence_intervals <- 
  as.data.frame(confint(model_1, method = "profile"))


tidy_fixed <- tidy(model_1, effects = "fixed") %>%
  select(term, estimate, std.error, statistic, p.value)


write.csv(tidy_fixed, "model_outputs/model_1_fixed.csv", row.names = FALSE)

data_used <- subset(NNAP_and_MBRRACE_data_to_analyse, 
                    !is.na(StabilisedNeonatalDeathRate_rank_norm) &
                    !is.na(mean_rank_norm) &
                    !is.na(Unit_level_highest_character))

data_used$prediction <- 
  predict(model_1, re.form = NA)

table <- table(data_used$Year)

length(data_used$Year)


sink("model_outputs/model_1.txt", split = TRUE)
print(summary(model_1))
performance::r2(model_1)
print("Confidence intervals of random effects:")

print(as.numeric(confidence_intervals[".sig01",][1]))
print(as.numeric(confidence_intervals[".sig01",][2]))

print("Data within each year:")

paste(paste(names(table), table, sep=":"), collapse = ", ")
sink()

regression_plot <-
ggplot(
  data=data_used, 
  aes(x=mean_rank_norm, y=StabilisedNeonatalDeathRate_rank_norm, colour=Unit_level_highest_character)) + 
  scale_colour_manual(values = c(
  "1" = "Orange",
  "2018" = "SkyBlue",
  "2019" = "#009E73",
  "2020" = "#F0E442",
  "2" = "#0072B2", 
  "2022" = "#D55E00",
  "3" = "#000000" )) +
  geom_point(size=0.5) +
  geom_line(aes(y=prediction), linewidth=1) +
  scale_y_continuous(
  limits = c(0, 1),
  breaks = seq(0, 1, by = 0.2),
  labels = scales::label_number(accuracy = 0.1)
) +
  scale_x_continuous(
  limits = c(0, 1),
  breaks = seq(0, 1, by = 0.2),
  labels = scales::label_number(accuracy = 0.1)
) +
  coord_cartesian(
    xlim = c(0, 1),
    ylim = c(0, 1)
    ) +
  theme_minimal() +
  theme(  
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank())
regression_plot
ggsave(filename = paste0(
  "regression_plot_mortality",
  ".png"),
         path = "histograms",
         plot = regression_plot + 
    theme(axis.title=element_blank(), 
         plot.title=element_blank(), 
         plot.subtitle=element_blank(),
         plot.legend=element_blank(),
         legend.position="none"),,
         device = "png",
         width = 3,
         height = 3,
         limitsize = FALSE,
  bg = "white")
```

```{r}
library(lme4)
library(lmerTest)
library(ggplot2)
library(broom.mixed)
library(dplyr)
library(performance)

model_1_without_unit <- 
  lmer(
    StabilisedNeonatalDeathRate_rank_norm ~ 
                    mean_rank_norm +
                    (1 | Trust_name)  ,
    data=NNAP_and_MBRRACE_data_to_analyse)
summary(model_1_without_unit)
dir.create("model_outputs", showWarnings = FALSE)
confidence_intervals <- 
  as.data.frame(confint(model_1_without_unit, method = "profile"))

tidy_fixed <- tidy(model_1_without_unit, effects = "fixed") %>%
  select(term, estimate, std.error, statistic, p.value)

write.csv(tidy_fixed, "model_outputs/model_1_without_unit_fixed.csv", row.names = FALSE)

data_used <- subset(NNAP_and_MBRRACE_data_to_analyse, 
                    !is.na(StabilisedNeonatalDeathRate_rank_norm) &
                    !is.na(mean_rank_norm))

data_used$prediction <- 
  predict(model_1_without_unit, re.form = NA)

table <- table(data_used$Year)

length(data_used$Year)

sink("model_outputs/model_1_without_unit.txt", split = TRUE)
print(summary(model_1_without_unit))
performance::r2(model_1_without_unit)
print("Confidence intervals of random effects:")

print(as.numeric(confidence_intervals[".sig01",][1]))
print(as.numeric(confidence_intervals[".sig01",][2]))

print("Data within each year:")

paste(paste(names(table), table, sep=":"), collapse = ", ")
sink()

regression_plot <-
ggplot(
  data=data_used, 
  aes(x=mean_rank_norm, y=StabilisedNeonatalDeathRate_rank_norm, colour=Unit_level_highest_character)) + 
  scale_colour_manual(values = c(
  "1" = "Orange",
  "2018" = "SkyBlue",
  "2019" = "#009E73",
  "2020" = "#F0E442",
  "2" = "#0072B2",
  "2022" = "#D55E00",
  "3" = "#000000" 
  )) +
  geom_point(size=0.5) +
  geom_line(aes(y=prediction), linewidth=1, linetype="dashed", colour="darkred") +
  scale_y_continuous(
  limits = c(0, 1),
  breaks = seq(0, 1, by = 0.2),
  labels = scales::label_number(accuracy = 0.1)
) +
  scale_x_continuous(
  limits = c(0, 1),
  breaks = seq(0, 1, by = 0.2),
  labels = scales::label_number(accuracy = 0.1)
) +
  coord_cartesian(
    xlim = c(0, 1),
    ylim = c(0, 1)
    ) +
  theme_minimal() +
  theme(  
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank())
regression_plot
ggsave(filename = paste0(
  "regression_plot_mortality_without_unit",
  ".png"),
         path = "histograms",
         plot = regression_plot + 
    theme(axis.title=element_blank(), 
         plot.title=element_blank(), 
         plot.subtitle=element_blank(),
         plot.legend=element_blank(),
         legend.position="none"),,
         device = "png",
         width = 3,
         height = 3,
         limitsize = FALSE,
  bg = "white")
```


```{r, NOT TO USE table 2 overall mortality on overall rank multilevel illustrative model draft 2 interaction effect on level of unit individual lines}
library(lme4)
library(lmerTest)
library(ggplot2)
library(broom.mixed)
library(dplyr)
library(performance)

model_1_redraft <- 
  lmer(
    StabilisedNeonatalDeathRate_rank_norm ~ 
                    mean_rank_norm *
                    Unit_level_highest_character +
                    (1 | Trust_name)  ,
    data=NNAP_and_MBRRACE_data_to_analyse)

summary(model_1)
summary(model_1_redraft)

library(emmeans)

print("You use the emtrends standard deviations to explain the combined slope standard errors")
emmeans(model_1_redraft,
        ~ Unit_level_highest_character,
        at = list(mean_rank_norm = 0))

emtrends(model_1_redraft,
         ~ Unit_level_highest_character,
         var = "mean_rank_norm")


dir.create("model_outputs", showWarnings = FALSE)
confidence_intervals <- 
  as.data.frame(confint(model_1_redraft, method = "profile"))

tidy_fixed <- tidy(model_1_redraft, effects = "fixed") %>%
  select(term, estimate, std.error, statistic, p.value)

write.csv(tidy_fixed, "model_outputs/model_1_redraft_fixed.csv", row.names = FALSE)

data_used <- subset(NNAP_and_MBRRACE_data_to_analyse, 
                    !is.na(StabilisedNeonatalDeathRate_rank_norm) &
                    !is.na(mean_rank_norm) &
                    !is.na(Unit_level_highest_character))

data_used$prediction <- 
  predict(model_1_redraft, re.form = NA)

table <- table(data_used$Year)

length(data_used$Year)

sink("model_outputs/model_1_redraft.txt", split = TRUE)
print(summary(model_1_redraft))
performance::r2(model_1_redraft)
print("Confidence intervals of random effects:")

print(as.numeric(confidence_intervals[".sig01",][1]))
print(as.numeric(confidence_intervals[".sig01",][2]))

print("Data within each year:")

paste(paste(names(table), table, sep=":"), collapse = ", ")
sink()

regression_plot <-
ggplot(
  data=data_used, 
  aes(x=mean_rank_norm, y=StabilisedNeonatalDeathRate_rank_norm, colour=Unit_level_highest_character)) + 
  scale_colour_manual(values = c(
  "1" = "Orange",
  "2018" = "SkyBlue",
  "2019" = "#009E73", ##009E73 is blueish green
  "2020" = "#F0E442", #yellow #F0E442
  "2" = "#0072B2", #blue #0072B2
  "2022" = "#D55E00", ##D55E00 vermillion
  "3" = "#000000" #black
  )) +
  geom_point(size=0.5) +
  geom_line(aes(y=prediction), linewidth=1) +
  theme_minimal() #+
#  geom_smooth(method="lm")
regression_plot
ggsave(filename = paste0(
  "regression_plot_mortality_redraft_not_to_use",
  ".png"),
         path = "histograms",
         plot = regression_plot + 
    theme(axis.title=element_blank(), 
         plot.title=element_blank(), 
         plot.subtitle=element_blank(),
         plot.legend=element_blank()),,
         device = "png",
         width = 6,
         height = 3,
         limitsize = FALSE,
  bg = "white")
```

********************************
ranking tables
********************************

```{r}
library(dplyr)
library(tidyr)

for (metric_to_rank_by in c(
  "StabilisedNeonatalDeathRate_no_ties",
  "mean_rank_norm_no_ties",
  "mean_perinatal_rank_norm_no_ties",
  "mean_morbidity_rank_norm_no_ties",
  "mean_of_perinatal_and_morbidity_rank_norm_no_ties",
  "bpd_crude_pct_no_ties",
  "NEC_crude_pct_no_ties",
  "sepsis_crude_pct_no_zeros_no_ties",
  "IVH_crude_pct_no_ties",
  "cPVL_crude_pct_no_ties"
)) {
  
  title <- switch(metric_to_rank_by,
                  "StabilisedNeonatalDeathRate_no_ties" = "Stabilised neonatal death rate",
                  "mean_rank_norm_no_ties" = "Normalised rank of mean of all NNAP metrics",
                  "mean_perinatal_rank_norm_no_ties" = "Normalised rank of mean of perinatal NNAP metrics",
                  "mean_morbidity_rank_norm_no_ties" = "Normalised rank of mean of morbidity NNAP metrics",
                  "mean_of_perinatal_and_morbidity_rank_norm_no_ties" = "Normalised rank of mean of the mean of perinatal and morbidity metrics",
                  "bpd_crude_pct_no_ties" = "Normalised rank of BPD percentage",
                  "NEC_crude_pct_no_ties" = "Normalised rank of NEC percentage",
                  "sepsis_crude_pct_no_zeros_no_ties" = "Normalised rank of sepsis percentage excluding zeros",
                  "IVH_crude_pct_no_ties" = "Normalised rank of IVH percentage",
                  "cPVL_crude_pct_no_ties" = "Normalised rank of cPVL percentage"
  )

    rank_col_name <- paste0("Rank: ", title)
  
  abbreviations_to_join <- read.csv("abbreviations_to_load/Abbreviations_to_load.csv")
  
NNAP_and_MBRRACE_data_to_analyse_with_abbreviations <-
  dplyr::left_join(
    NNAP_and_MBRRACE_data_to_analyse,
    abbreviations_to_join,
    by = c("Trust_name" = "Trust")
  )

rank_table <- NNAP_and_MBRRACE_data_to_analyse_with_abbreviations %>%
    filter(Year %in% 2017:2023) %>%
    select(
      Year,
      !!rank_col_name := !!sym(metric_to_rank_by),
      Abbreviation
    ) %>%
    distinct() %>%
    group_by(!!sym(rank_col_name), Year) %>%
    summarise(Abbreviation = paste(Abbreviation, collapse = ", "), .groups = "drop") %>%
    pivot_wider(
      names_from = Year,
      values_from = Abbreviation
    ) %>%
    arrange(!!sym(rank_col_name))

rank_table <- rank_table %>%
  mutate(
    !!rank_col_name := as.character(!!sym(rank_col_name)),
    !!rank_col_name := replace_na(!!sym(rank_col_name), "No data")
  )
  
  write.csv(
    rank_table, 
    file = paste0("ranking_tables/rank_by_", metric_to_rank_by, ".csv"), 
    row.names = FALSE
  )
  
ft <- flextable(rank_table)

ft <- ft %>%
  theme_vanilla() %>%
  align(align = "center", part = "header") %>%
  autofit()

centered_paragraph <- 
  fp_par(text.align = "center")
font_properties <- fp_text(font.size = 14, bold = TRUE, color = "black")
doc <- 
  read_docx() %>%
  body_add_flextable(ft)
  
  dir.create("ranking_tables", showWarnings = F)
  
print(doc, 
      target = paste0("ranking_tables/", "rankings_by_", metric_to_rank_by, ".docx"))


}
```

```{r, print a key to our abbreviations}
look_at_abbreviations <-
  NNAP_and_MBRRACE_data_to_analyse_with_abbreviations %>%
  select(Abbreviation, Trust_name) %>%
  distinct() %>%
  arrange(Abbreviation)

ft <- flextable(look_at_abbreviations)

ft <- ft %>%
  theme_vanilla() %>%
  align(align = "center", part = "header") %>%
  autofit()

centered_paragraph <- 
  fp_par(text.align = "center")
font_properties <- fp_text(font.size = 14, bold = TRUE, color = "black")
doc <- 
  read_docx() %>%
  body_add_flextable(ft) 
  
  dir.create("ranking_tables", showWarnings = F)
  
print(doc, 
      target = paste0("ranking_tables/", "key_to_trusts", ".docx"))

```
